---
title: "tula() codebook mode — tests"
format: html
---

```{r setup}
devtools::load_all(".")
```

## Test 1: Basic numeric data frame (mtcars)

All variables are numeric with many unique values, so they should show
continuous mode (mean, SD, percentiles).

```{r}
tula(mtcars, codebook = TRUE)
```

## Test 2: Single vector

```{r}
tula(mtcars$mpg, codebook = TRUE)
```

## Test 3: Data frame with factors

```{r}
df_fac <- data.frame(
  cyl = factor(mtcars$cyl),
  gear = factor(mtcars$gear),
  mpg = mtcars$mpg
)
tula(df_fac, codebook = TRUE)
```

## Test 4: Data frame with character column

```{r}
df_chr <- data.frame(
  name = rownames(mtcars),
  mpg = mtcars$mpg,
  stringsAsFactors = FALSE
)
tula(df_chr, codebook = TRUE)
```

## Test 5: Numeric variable with few unique values (tabulation mode)

`cyl` has only 3 unique values, `gear` has 3, `am` has 2.

```{r}
tula(mtcars[, c("cyl", "gear", "am", "mpg")], codebook = TRUE)
```

## Test 6: Haven-labelled data

```{r}
library(haven)
gss <- data.frame(
  trust = labelled(
    c(1, 1, 2, 2, 1, 3, 1, 2, 2, 1),
    c("Can trust" = 1, "Can't be too careful" = 2, "Depends" = 3),
    label = "Can people be trusted"
  ),
  happy = labelled(
    c(1, 2, 3, 1, 2, 2, 3, 1, 1, 2),
    c("Very happy" = 1, "Pretty happy" = 2, "Not too happy" = 3),
    label = "General happiness"
  ),
  age = labelled(
    c(35, 42, 28, 55, 61, 33, 47, 29, 38, 50),
    label = "Age of respondent"
  )
)
tula(gss, codebook = TRUE)
```

## Test 7: Logical variable

```{r}
df_log <- data.frame(
  is_auto = mtcars$am == 1,
  mpg = mtcars$mpg
)
tula(df_log, codebook = TRUE)
```

## Test 8: Mixed data frame

```{r}
df_mix <- data.frame(
  name = c("Alice", "Bob", "Charlie", "Diana", "Eve"),
  score = c(85.5, 92.3, 78.1, 95.7, 88.2),
  grade = factor(c("B", "A", "C", "A", "B"), levels = c("A", "B", "C")),
  passed = c(TRUE, TRUE, FALSE, TRUE, TRUE),
  stringsAsFactors = FALSE
)
tula(df_mix, codebook = TRUE)
```

## Test 9: Column with NAs

```{r}
df_na <- data.frame(
  x = c(1, 2, 3, NA, 5, NA, 7, 8, 9, 10),
  y = c("a", "b", NA, "d", "e", NA, "g", "h", "i", "j"),
  stringsAsFactors = FALSE
)
tula(df_na, codebook = TRUE)
```

## Test 10: Width parameter

```{r}
tula(mtcars[, 1:3], codebook = TRUE, width = 60)
```

## Test 11: Ordered factor

```{r}
df_ord <- data.frame(
  satisfaction = ordered(c("Low", "Medium", "High", "Medium", "High",
                           "Low", "High", "Medium", "Low", "High"),
                         levels = c("Low", "Medium", "High"))
)
tula(df_ord, codebook = TRUE)
```

## Test 12: Ordered factor with many levels (truncation)

Ordered factors with more than 9 levels should show the first 8, then `...`,
then the highest level. Unordered factors should never truncate.

```{r}
# Ordered with 15 levels → should truncate
lvls <- c("Strongly disagree", "Disagree", "Slightly disagree",
          "Neutral minus", "Neutral", "Neutral plus",
          "Slightly agree", "Agree", "Mostly agree",
          "Strongly agree", "Very strongly agree",
          "Completely agree", "Totally agree",
          "Absolutely agree", "Cannot agree more")
df_many <- data.frame(
  agreement = ordered(sample(lvls, 60, replace = TRUE), levels = lvls)
)
tula(df_many, codebook = TRUE)
```

```{r}
# Unordered with 12 levels → should NOT truncate
df_unord <- data.frame(
  color = factor(sample(paste0("Color_", 1:12), 50, replace = TRUE))
)
tula(df_unord, codebook = TRUE)
```

## Test 13: Existing tula() summarize still works

```{r}
tula(mtcars)
```
