---
title: "tulatab crosstab — Visual Test Script"
format:
  html:
    embed-resources: true
    toc: true
    document-css: false
---

```{r setup, include=FALSE}
devtools::load_all(".", quiet = TRUE)
```

## Test 1 — Basic factor x factor crosstab

```{r}
df <- data.frame(
  color = factor(c("red","blue","red","green","blue","red","green","blue","red","blue"),
                 levels = c("red","blue","green")),
  size  = factor(c("S","M","L","S","M","L","S","M","L","S"),
                 levels = c("S","M","L"))
)
tulatab(color, size, data = df)
```

## Test 2 — Numeric x numeric

```{r}
tulatab(mtcars$vs, mtcars$cyl)
```

## Test 3 — NSE with data=

```{r}
tulatab(vs, cyl, data = mtcars)
```

## Test 4 — Column percentages (default)

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "col")
```

## Test 5 — Row percentages

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "row")
```

## Test 6 — Cell percentages

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "cell")
```

## Test 7 — No percentages (pct = NULL)

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = NULL)
```

## Test 8 — freq = FALSE (column pct only)

```{r}
tulatab(mtcars$vs, mtcars$cyl, freq = FALSE)
```

## Test 9 — freq = FALSE, pct = NULL (blank cells)

```{r}
tulatab(mtcars$vs, mtcars$cyl, freq = FALSE, pct = NULL)
```

## Test 10 — Missing in both variables

```{r}
df2 <- data.frame(
  y = factor(c("a","b","a","b","a",NA,"b",NA,"a","b"), levels = c("a","b")),
  x = factor(c("X","Y",NA,"X","Y","X",NA,"Y","X","Y"), levels = c("X","Y"))
)
tulatab(y, x, data = df2, missing = TRUE)
```

## Test 11 — Sort by marginals

```{r}
df3 <- data.frame(
  y = factor(c(rep("rare",2), rep("common",8), rep("mid",5)),
             levels = c("rare","mid","common")),
  x = factor(c(rep("A",3), rep("B",5), rep("C",7)),
             levels = c("A","B","C"))
)
tulatab(y, x, data = df3, sort = TRUE)
```

## Test 12 — Haven-labelled (labels win when both TRUE)

```{r}
library(haven)
trust <- labelled(
  c(0,0,0,1,1,0,0,1,0,1,0,0,0,1,0,1,0,0,1,0),
  labels = c("no" = 0, "yes" = 1),
  label = "can people be trusted"
)
degree <- labelled(
  c(1,2,3,1,2,4,5,3,2,4,1,5,2,3,4,1,2,5,3,4),
  labels = c("less than high school" = 1, "high school diploma" = 2,
             "associate/junior college" = 3, "bachelor's degree" = 4,
             "graduate degree" = 5),
  label = "r's highest degree"
)
tulatab(trust, degree)
```

## Test 13 — Haven-labelled (value=TRUE, label=FALSE)

```{r}
tulatab(trust, degree, value = TRUE, label = FALSE)
```

## Test 14 — Haven-labelled (value=FALSE, label=TRUE)

```{r}
tulatab(trust, degree, value = FALSE, label = TRUE)
```

## Test 15 — Multi-panel overflow (many columns)

```{r}
set.seed(42)
n <- 200
df_wide <- data.frame(
  trust = factor(sample(c("no","yes"), n, replace = TRUE, prob = c(0.7, 0.3))),
  score = sample(16:32, n, replace = TRUE)
)
tulatab(trust, score, data = df_wide, width = 80)
```

## Test 16 — Multi-panel at narrow width

```{r}
tulatab(mtcars$vs, mtcars$cyl, width = 60)
```

## Test 17 — One-way backward compatibility (direct vector)

```{r}
tulatab(mtcars$cyl)
```

## Test 18 — One-way backward compatibility (NSE)

```{r}
tulatab(cyl, data = mtcars)
```

## Test 19 — One-way ordered factor

```{r}
tulatab(factor(mtcars$gear, ordered = TRUE))
```

## Test 20 — Character x character

```{r}
df_char <- data.frame(
  pet  = c("cat","dog","cat","dog","cat","bird","dog","cat"),
  food = c("wet","dry","wet","wet","dry","dry","wet","dry"),
  stringsAsFactors = FALSE
)
tulatab(pet, food, data = df_char)
```

## Test 21 — Row pct with freq=FALSE

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "row", freq = FALSE)
```

## Test 22 — Cell pct with freq=FALSE

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "cell", freq = FALSE)
```
