---
title: "tulatab crosstab — Visual Test Script"
format:
  html:
    embed-resources: true
    toc: true
    document-css: false
---

```{r setup, include=FALSE}
devtools::load_all(".", quiet = TRUE)
```

## Test 1 — Basic factor x factor crosstab

```{r}
df <- data.frame(
  color = factor(c("red","blue","red","green","blue","red","green","blue","red","blue"),
                 levels = c("red","blue","green")),
  size  = factor(c("S","M","L","S","M","L","S","M","L","S"),
                 levels = c("S","M","L"))
)
tulatab(color, size, data = df)
```

## Test 2 — Numeric x numeric

```{r}
tulatab(mtcars$vs, mtcars$cyl)
```

## Test 3 — NSE with data=

```{r}
tulatab(vs, cyl, data = mtcars)
```

## Test 4 — Column percentages (default)

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "col")
```

## Test 5 — Row percentages

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "row")
```

## Test 6 — Cell percentages

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "cell")
```

## Test 7 — No percentages (pct = NULL)

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = NULL)
```

## Test 8 — freq = FALSE (column pct only)

```{r}
tulatab(mtcars$vs, mtcars$cyl, freq = FALSE)
```

## Test 9 — freq = FALSE, pct = NULL (blank cells)

```{r}
tulatab(mtcars$vs, mtcars$cyl, freq = FALSE, pct = NULL)
```

## Test 10 — Missing in both variables

```{r}
df2 <- data.frame(
  y = factor(c("a","b","a","b","a",NA,"b",NA,"a","b"), levels = c("a","b")),
  x = factor(c("X","Y",NA,"X","Y","X",NA,"Y","X","Y"), levels = c("X","Y"))
)
tulatab(y, x, data = df2, missing = TRUE)
```

## Test 11 — Sort by marginals

```{r}
df3 <- data.frame(
  y = factor(c(rep("rare",2), rep("common",8), rep("mid",5)),
             levels = c("rare","mid","common")),
  x = factor(c(rep("A",3), rep("B",5), rep("C",7)),
             levels = c("A","B","C"))
)
tulatab(y, x, data = df3, sort = TRUE)
```

## Test 12 — Haven-labelled (labels win when both TRUE)

```{r}
library(haven)
trust <- labelled(
  c(0,0,0,1,1,0,0,1,0,1,0,0,0,1,0,1,0,0,1,0),
  labels = c("no" = 0, "yes" = 1),
  label = "can people be trusted"
)
degree <- labelled(
  c(1,2,3,1,2,4,5,3,2,4,1,5,2,3,4,1,2,5,3,4),
  labels = c("less than high school" = 1, "high school diploma" = 2,
             "associate/junior college" = 3, "bachelor's degree" = 4,
             "graduate degree" = 5),
  label = "r's highest degree"
)
tulatab(trust, degree)
```

## Test 13 — Haven-labelled (value=TRUE, label=FALSE)

```{r}
tulatab(trust, degree, value = TRUE, label = FALSE)
```

## Test 14 — Haven-labelled (value=FALSE, label=TRUE)

```{r}
tulatab(trust, degree, value = FALSE, label = TRUE)
```

## Test 15 — Multi-panel overflow (many columns)

```{r}
set.seed(42)
n <- 200
df_wide <- data.frame(
  trust = factor(sample(c("no","yes"), n, replace = TRUE, prob = c(0.7, 0.3))),
  score = sample(16:32, n, replace = TRUE)
)
tulatab(trust, score, data = df_wide, width = 80)
```

## Test 16 — Multi-panel at narrow width

```{r}
tulatab(mtcars$vs, mtcars$cyl, width = 60)
```

## Test 17 — One-way backward compatibility (direct vector)

```{r}
tulatab(mtcars$cyl)
```

## Test 18 — One-way backward compatibility (NSE)

```{r}
tulatab(cyl, data = mtcars)
```

## Test 19 — One-way ordered factor

```{r}
tulatab(factor(mtcars$gear, ordered = TRUE))
```

## Test 20 — Character x character

```{r}
df_char <- data.frame(
  pet  = c("cat","dog","cat","dog","cat","bird","dog","cat"),
  food = c("wet","dry","wet","wet","dry","dry","wet","dry"),
  stringsAsFactors = FALSE
)
tulatab(pet, food, data = df_char)
```

## Test 21 — Row pct with freq=FALSE

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "row", freq = FALSE)
```

## Test 22 — Cell pct with freq=FALSE

```{r}
tulatab(mtcars$vs, mtcars$cyl, pct = "cell", freq = FALSE)
```

## Test 23 — by= with numeric grouping variable (NSE)

```{r}
tulatab(vs, cyl, data = mtcars, by = am)
```

## Test 24 — by= with factor grouping variable

```{r}
df_by <- data.frame(
  outcome = factor(c("pass","fail","pass","fail","pass","pass","fail","pass",
                      "fail","pass","pass","fail"),
                   levels = c("pass","fail")),
  method  = factor(c("A","B","A","B","A","B","A","B","A","B","A","B"),
                   levels = c("A","B")),
  group   = factor(c("ctrl","ctrl","ctrl","ctrl","ctrl","ctrl",
                      "treat","treat","treat","treat","treat","treat"),
                   levels = c("ctrl","treat"))
)
tulatab(outcome, method, data = df_by, by = group)
```

## Test 25 — by= with row percentages

```{r}
tulatab(vs, cyl, data = mtcars, by = am, pct = "row")
```

## Test 26 — by= with missing in the by-variable

```{r}
df_bymiss <- data.frame(
  y = factor(c("a","b","a","b","a","b","a","b","a","b"),
             levels = c("a","b")),
  x = factor(c("X","Y","X","Y","X","Y","X","Y","X","Y"),
             levels = c("X","Y")),
  g = factor(c("m","m","f","f","m", NA, "f", NA, "m","f"),
             levels = c("f","m"))
)
tulatab(y, x, data = df_bymiss, by = g, missing = TRUE)
```

## Test 27 — by= with haven-labelled grouping variable

```{r}
library(haven)
trust <- labelled(
  c(0,0,0,1,1,0,0,1,0,1,0,0,0,1,0,1,0,0,1,0),
  labels = c("no" = 0, "yes" = 1),
  label = "can people be trusted"
)
degree <- labelled(
  c(1,2,3,1,2,4,5,3,2,4,1,5,2,3,4,1,2,5,3,4),
  labels = c("less than high school" = 1, "high school diploma" = 2,
             "associate/junior college" = 3, "bachelor's degree" = 4,
             "graduate degree" = 5),
  label = "r's highest degree"
)
sex <- labelled(
  c(1,2,1,2,1,2,1,2,1,2,1,2,1,2,1,2,1,2,1,2),
  labels = c("male" = 1, "female" = 2),
  label = "respondent's sex"
)
tulatab(trust, degree, by = sex)
```

## Test 28 — by= with sort

```{r}
tulatab(vs, cyl, data = mtcars, by = am, sort = TRUE)
```

## Test 29 — by= with freq=FALSE

```{r}
tulatab(vs, cyl, data = mtcars, by = am, freq = FALSE)
```

## Test 30 — mean= basic (NSE)

Mean of mpg by cyl × am. Each cell shows mean on top, N on bottom.

```{r}
tulatab(cyl, am, data = mtcars, mean = mpg)
```

## Test 31 — mean= with direct vectors

```{r}
tulatab(mtcars$cyl, mtcars$am, mean = mtcars$mpg)
```

## Test 32 — mean= with by=

Separate mean tables per vs level.

```{r}
tulatab(cyl, am, data = mtcars, mean = mpg, by = vs)
```

## Test 33 — mean= with NAs in the mean variable

N should reflect only non-missing values.

```{r}
d <- mtcars
d$mpg2 <- d$mpg
d$mpg2[c(1, 5, 10, 15, 20, 25)] <- NA
tulatab(cyl, am, data = d, mean = mpg2)
```

## Test 34 — mean= with sort=TRUE

Rows and columns sorted by descending marginal counts.

```{r}
tulatab(cyl, am, data = mtcars, mean = mpg, sort = TRUE)
```

## Test 35 — mean= silently ignores pct and freq

Setting pct="row" and freq=FALSE should have no effect when mean= is specified.

```{r}
tulatab(cyl, am, data = mtcars, mean = mpg, pct = "row", freq = FALSE)
```

## Test 36 — mean= one-way mode error

```{r, error=TRUE}
tulatab(cyl, data = mtcars, mean = mpg)
```

## Test 37 — mean= non-numeric error

```{r, error=TRUE}
d <- mtcars
d$carname <- rownames(mtcars)
tulatab(cyl, am, data = d, mean = carname)
```
