---
title: "fixest support tests"
format: html
---

```{r setup}
devtools::load_all(".")
library(fixest)
```

## Test 1: Basic feols (no FE)

```{r}
m1 <- feols(mpg ~ wt + hp, data = mtcars)
cat("--- summary() ---\n")
summary(m1)
cat("\n--- tula() ---\n")
tula(m1)
```

## Test 2: feols with fixed effects

```{r}
m2 <- feols(mpg ~ wt + hp | cyl, data = mtcars)
cat("--- summary() ---\n")
summary(m2)
cat("\n--- tula() ---\n")
tula(m2)
```

## Test 3: feols with multiple FEs

```{r}
m3 <- feols(mpg ~ wt | cyl + gear, data = mtcars)
cat("--- summary() ---\n")
summary(m3)
cat("\n--- tula() ---\n")
tula(m3)
```

## Test 4: feols with i() factor interaction

```{r}
m4 <- feols(mpg ~ wt + i(cyl, ref = 4), data = mtcars)
cat("--- summary() ---\n")
summary(m4)
cat("\n--- tula() ---\n")
tula(m4)
```

## Test 5: feols with factor()

```{r}
m5 <- feols(mpg ~ wt + factor(cyl), data = mtcars)
cat("--- summary() ---\n")
summary(m5)
cat("\n--- tula() ---\n")
tula(m5)
```

## Test 6: Wide output with CIs

```{r}
cat("--- summary() ---\n")
summary(m2)
cat("\n--- tula(wide = TRUE) ---\n")
tula(m2, wide = TRUE)
```

## Test 7: Robust SEs

```{r}
cat("--- summary(vcov = 'hetero') ---\n")
summary(m2, vcov = "hetero")
cat("\n--- tula(robust = TRUE) ---\n")
tula(m2, robust = TRUE)
```

## Test 8: Cluster SEs

```{r}
cat("--- summary(cluster = ~gear) ---\n")
summary(m2, cluster = ~gear)
cat("\n--- tula(cluster = 'gear') ---\n")
tula(m2, cluster = "gear")
```

## Test 9: feglm (logit)

```{r}
m6 <- feglm(am ~ wt + hp | cyl, data = mtcars, family = binomial)
cat("--- summary() ---\n")
summary(m6)
cat("\n--- tula() ---\n")
tula(m6)
```

## Test 10: fepois

```{r}
set.seed(42)
count_data <- data.frame(
  y = rpois(200, lambda = 3),
  x1 = rnorm(200),
  x2 = rnorm(200),
  g = sample(1:10, 200, replace = TRUE)
)
m7 <- fepois(y ~ x1 + x2 | g, data = count_data)
cat("--- summary() ---\n")
summary(m7)
cat("\n--- tula() ---\n")
tula(m7)
```

## Test 11: fenegbin

```{r}
m8 <- fenegbin(y ~ x1 + x2 | g, data = count_data)
cat("--- summary() ---\n")
summary(m8)
cat("\n--- tula() ---\n")
tula(m8)
```

## Test 12: exp = TRUE with fepois

```{r}
cat("--- summary() ---\n")
summary(m7)
cat("\n--- tula(exp = TRUE) ---\n")
tula(m7, exp = TRUE)
```

## Test 13: Existing tula(lm) still works

```{r}
m_lm <- lm(mpg ~ wt, data = mtcars)
cat("--- summary() ---\n")
summary(m_lm)
cat("\n--- tula() ---\n")
tula(m_lm)
```

## Test 14: ref = TRUE with i()

```{r}
cat("--- summary() ---\n")
summary(m4)
cat("\n--- tula(ref = TRUE) ---\n")
tula(m4, ref = TRUE)
```

## Test 15: fixest_multi should error gracefully

```{r, error=TRUE}
m_multi <- feols(mpg ~ wt | csw(cyl, gear), data = mtcars)
tula(m_multi)
```
