---
title: "tula — Interaction Terms Exploration"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
devtools::load_all(".")
set.seed(42)
```

This file explores how `tula()` currently handles models with interaction
(multiplicative) terms, across a variety of scenarios. The goal is to document
current behavior and identify what changes (if any) might be desirable.

---

## 1 — Numeric × Numeric interaction

The simplest case: two continuous predictors crossed with `*`.
R creates three terms: the two main effects plus their product (`cyl:wt`).

```{r}
#| echo: false
m1 <- lm(mpg ~ cyl * wt, data = mtcars)
```

```{r}
summary(m1)$coefficients
```

```{r}
tula(m1)
```

Wide:

```{r}
tula(m1, wide = TRUE)
```

---

## 2 — Numeric × Numeric: explicit colon syntax

Same model as Section 1 written with explicit `+` and `:` instead of `*`.
Verifies that both formula styles produce identical output.

```{r}
#| echo: false
m2 <- lm(mpg ~ cyl + wt + cyl:wt, data = mtcars)
```

```{r}
tula(m2)
```

---

## 3 — Factor × Numeric interaction

One factor and one continuous predictor crossed with `*`.
R creates main effects for both plus separate slopes (`factor:numeric`) for
each non-reference factor level.

```{r}
#| echo: false
m3 <- lm(mpg ~ factor(cyl) * wt, data = mtcars)
```

```{r}
summary(m3)$coefficients
```

```{r}
tula(m3)
```

With ref = TRUE:

```{r}
tula(m3, ref = TRUE)
```

Wide:

```{r}
tula(m3, wide = TRUE)
```

---

## 4 — Factor × Numeric: named factor variable (not inline)

Same as Section 3 but the factor is stored as a named column, which can
affect how labels appear.

```{r}
#| echo: false
df4 <- mtcars
df4$cyl_f <- factor(mtcars$cyl)
m4 <- lm(mpg ~ cyl_f * wt, data = df4)
```

```{r}
summary(m4)$coefficients
```

```{r}
tula(m4)
```

With ref = TRUE:

```{r}
tula(m4, ref = TRUE)
```

---

## 5 — Factor × Factor interaction

Two factor variables crossed with `*`.
Produces main-effect groups for each factor plus interaction dummy rows.

```{r}
#| echo: false
m5 <- lm(mpg ~ factor(cyl) * factor(am), data = mtcars)
```

```{r}
summary(m5)$coefficients
```

```{r}
tula(m5)
```

With ref = TRUE:

```{r}
tula(m5, ref = TRUE)
```

Wide:

```{r}
tula(m5, wide = TRUE)
```

---

## 6 — Factor × Factor: named factor variables

Same as Section 5 but using pre-created named factor columns.

```{r}
#| echo: false
df6 <- mtcars
df6$cyl_f <- factor(mtcars$cyl)
df6$am_f  <- factor(mtcars$am, labels = c("automatic", "manual"))
m6 <- lm(mpg ~ cyl_f * am_f, data = df6)
```

```{r}
summary(m6)$coefficients
```

```{r}
tula(m6)
```

With ref = TRUE:

```{r}
tula(m6, ref = TRUE)
```

---

## 7 — Interaction only (no main effect for one term)

Using `:` directly to include an interaction term without its component
main effect (uncommon but valid). Shows how tula handles a model where
the term labels don't include one of the constituent variables.

```{r}
#| echo: false
# wt main effect only; cyl appears only in the interaction
m7 <- lm(mpg ~ wt + cyl:wt, data = mtcars)
```

```{r}
summary(m7)$coefficients
```

```{r}
tula(m7)
```

---

## 8 — Three-way numeric interaction

A three-way `*` expansion among continuous predictors, producing all two-way
and the three-way interaction terms.

```{r}
#| echo: false
m8 <- lm(mpg ~ cyl * wt * hp, data = mtcars)
```

```{r}
summary(m8)$coefficients
```

```{r}
tula(m8)
```

Wide:

```{r}
tula(m8, wide = TRUE)
```

---

## 9 — Factor × Numeric with additional covariates

A realistic model: a factor × numeric interaction alongside other predictors.

```{r}
#| echo: false
df9 <- mtcars
df9$transmission <- factor(mtcars$am, labels = c("automatic", "manual"))
m9 <- lm(mpg ~ transmission * wt + hp + qsec, data = df9)
```

```{r}
summary(m9)$coefficients
```

```{r}
tula(m9)
```

With ref = TRUE:

```{r}
tula(m9, ref = TRUE)
```

Wide:

```{r}
tula(m9, wide = TRUE)
```

---

## 10 — Long interaction term names

Interaction terms formed from long variable names, to see how truncation
applies to terms like `long_name_a:long_name_b`.

```{r}
#| echo: false
df10 <- mtcars
df10$fuel_efficiency_rating   <- mtcars$mpg + rnorm(32, 0, 1)
df10$engine_displacement_liters <- mtcars$disp / 61.024
df10$vehicle_curb_weight_lbs    <- mtcars$wt * 1000
df10$transmission_type          <- factor(mtcars$am, labels = c("automatic", "manual"))
m10 <- lm(mpg ~ fuel_efficiency_rating * engine_displacement_liters +
                vehicle_curb_weight_lbs + transmission_type,
           data = df10)
```

```{r}
summary(m10)$coefficients
```

```{r}
tula(m10)
```

Wide:

```{r}
tula(m10, wide = TRUE)
```

width = Inf:

```{r}
tula(m10, width = Inf)
```

---

## 11 — GLM with interaction

A logistic regression with a factor × numeric interaction, to confirm behavior
carries over to GLM models.

```{r}
#| echo: false
m11 <- glm(am ~ factor(cyl) * wt, data = mtcars, family = binomial)
```

```{r}
summary(m11)$coefficients
```

```{r}
tula(m11)
```

With ref = TRUE:

```{r}
tula(m11, ref = TRUE)
```

Wide:

```{r}
tula(m11, wide = TRUE)
```

---

## 12 — Polynomial terms (not an interaction, but related)

`I(x^2)` and `poly()` create derived numeric terms that are not interactions
but have non-standard names. Included for comparison.

```{r}
#| echo: false
m12a <- lm(mpg ~ wt + I(wt^2), data = mtcars)
```

```{r}
tula(m12a)
```

```{r}
#| echo: false
m12b <- lm(mpg ~ poly(wt, 2), data = mtcars)
```

```{r}
tula(m12b)
```

```{r}
#| echo: false
m12c <- lm(mpg ~ poly(wt, 2, raw = TRUE), data = mtcars)
```

```{r}
tula(m12c)
```
