---
title: "tula — Long Names Exploration"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
devtools::load_all(".")
```

This file explores how `tula()` handles long variable names and long factor
level names with the `width` option (default: `getOption("width")`, which
reflects the current R console width setting).

Each section shows output at the default width, at `width = Inf` (no cap,
full natural width), and where useful at a custom intermediate width.

---

## 1 — Long numeric predictor names

Variable names of increasing length, all numeric (no factor grouping).

```{r}
#| echo: false
df <- mtcars
df$displacement_cubic_inches  <- mtcars$disp
df$horsepower_net              <- mtcars$hp
df$rear_axle_ratio             <- mtcars$drat
df$weight_in_thousands_of_lbs  <- mtcars$wt

m <- lm(mpg ~ displacement_cubic_inches + horsepower_net +
               rear_axle_ratio + weight_in_thousands_of_lbs,
        data = df)
```

Narrow (default width = 79):

```{r}
tula(m)
```

Narrow (width = Inf):

```{r}
tula(m, width = Inf)
```

Wide (default width = 79):

```{r}
tula(m, wide = TRUE)
```

Wide (width = Inf):

```{r}
tula(m, wide = TRUE, width = Inf)
```

---

## 2 — Long factor variable name, short level names

The factor variable itself has a long name; the individual levels are short
(numeric strings).

```{r}
#| echo: false
df <- mtcars
df$number_of_cylinders <- factor(mtcars$cyl)

m <- lm(mpg ~ number_of_cylinders + wt, data = df)
```

Narrow:

```{r}
tula(m)
```

Narrow, ref = TRUE:

```{r}
tula(m, ref = TRUE)
```

Wide:

```{r}
tula(m, wide = TRUE)
```

Wide, ref = TRUE:

```{r}
tula(m, ref = TRUE, wide = TRUE)
```

---

## 3 — Short factor variable name, long level names

The factor variable name is short; the level labels themselves are long strings.

```{r}
#| echo: false
df <- data.frame(
  y   = c(2.1, 3.4, 1.9, 4.2, 3.1, 2.8, 3.9, 2.3, 4.1, 3.7,
           2.5, 3.2, 1.8, 4.0, 3.3, 2.6, 3.8, 2.2, 4.3, 3.5),
  grp = factor(rep(c(
    "Participants in the control condition",
    "Participants in the treatment condition A",
    "Participants in the treatment condition B",
    "Participants who withdrew from the study"
  ), 5)),
  x   = rnorm(20)
)

m <- lm(y ~ grp + x, data = df)
```

Narrow (default width = 79):

```{r}
tula(m)
```

Narrow (width = Inf):

```{r}
tula(m, width = Inf)
```

Narrow, ref = TRUE (default width = 79):

```{r}
tula(m, ref = TRUE)
```

Wide (default width = 79):

```{r}
tula(m, wide = TRUE)
```

Wide (width = Inf):

```{r}
tula(m, wide = TRUE, width = Inf)
```

---

## 4 — Long factor variable name AND long level names

Both the variable name and the level labels are long.

```{r}
#| echo: false
df <- data.frame(
  outcome              = c(2.1, 3.4, 1.9, 4.2, 3.1, 2.8, 3.9, 2.3, 4.1, 3.7,
                           2.5, 3.2, 1.8, 4.0, 3.3, 2.6, 3.8, 2.2, 4.3, 3.5),
  experimental_condition = factor(rep(c(
    "Randomized to control arm",
    "Randomized to low-dose treatment arm",
    "Randomized to high-dose treatment arm",
    "Randomized to combination treatment arm"
  ), 5)),
  baseline_score       = rnorm(20)
)

m <- lm(outcome ~ experimental_condition + baseline_score, data = df)
```

Narrow (default width = 79):

```{r}
tula(m)
```

Narrow (width = Inf):

```{r}
tula(m, width = Inf)
```

Narrow, ref = TRUE (default width = 79):

```{r}
tula(m, ref = TRUE)
```

Narrow, ref = TRUE (width = Inf):

```{r}
tula(m, ref = TRUE, width = Inf)
```

Wide (default width = 79):

```{r}
tula(m, wide = TRUE)
```

Wide (width = Inf):

```{r}
tula(m, wide = TRUE, width = Inf)
```

---

## 5 — Very long single variable name (no factor)

One predictor name that is extremely long on its own.

```{r}
#| echo: false
df <- mtcars
df$self_reported_fuel_efficiency_miles_per_gallon_city_cycle <- mtcars$mpg + rnorm(32, 0, 0.5)
df$vehicle_curb_weight_measured_in_thousands_of_pounds       <- mtcars$wt

m <- lm(mpg ~ self_reported_fuel_efficiency_miles_per_gallon_city_cycle +
               vehicle_curb_weight_measured_in_thousands_of_pounds,
        data = df)
```

Narrow (default width = 79):

```{r}
tula(m)
```

Narrow (width = Inf):

```{r}
tula(m, width = Inf)
```

Wide (default width = 79):

```{r}
tula(m, wide = TRUE)
```

Wide (width = Inf):

```{r}
tula(m, wide = TRUE, width = Inf)
```

---

## 6 — Long factor name with `factor()` inline in formula

Tests whether label-stripping of `factor()` wrapper still displays correctly
when the inner variable name is itself long.

```{r}
#| echo: false
df <- mtcars
df$transmission_type_coded <- mtcars$am
df$number_of_forward_gears <- mtcars$gear

m <- lm(mpg ~ factor(transmission_type_coded) +
               factor(number_of_forward_gears) + wt,
        data = df)
```

Narrow:

```{r}
tula(m)
```

Narrow, ref = TRUE:

```{r}
tula(m, ref = TRUE)
```

Wide:

```{r}
tula(m, wide = TRUE)
```

---

## 7 — Mix: one short name, one long name, one long factor

Realistic scenario with a mixture of name lengths.

```{r}
#| echo: false
df <- data.frame(
  y               = rnorm(120, 50, 10),
  age             = sample(18:65, 120, replace = TRUE),
  years_of_formal_education_completed = sample(8:20, 120, replace = TRUE),
  employment_status = factor(sample(c(
    "Employed full-time",
    "Employed part-time",
    "Unemployed and seeking work",
    "Not in the labor force"
  ), 120, replace = TRUE))
)

m <- lm(y ~ age + years_of_formal_education_completed + employment_status,
        data = df)
```

Narrow (default width = 79):

```{r}
tula(m)
```

Narrow (width = Inf):

```{r}
tula(m, width = Inf)
```

Narrow, ref = TRUE (default width = 79):

```{r}
tula(m, ref = TRUE)
```

Wide (default width = 79):

```{r}
tula(m, wide = TRUE)
```

Wide (width = Inf):

```{r}
tula(m, wide = TRUE, width = Inf)
```

---

## 8 — Extremely long level name (truncation check)

A single factor whose one level name is so long it may exceed the label column.
This tests whether/how truncation (the `~` suffix) kicks in.

```{r}
#| echo: false
df <- data.frame(
  y   = rnorm(30),
  grp = factor(rep(c(
    "A",
    "This is an extremely long factor level name that goes on and on and probably exceeds any reasonable column width",
    "B"
  ), 10)),
  x   = rnorm(30)
)

m <- lm(y ~ grp + x, data = df)
```

Narrow (default width = 79):

```{r}
tula(m)
```

Narrow (width = Inf -- no truncation):

```{r}
tula(m, width = Inf)
```

Narrow, ref = TRUE (default width = 79):

```{r}
tula(m, ref = TRUE)
```

Wide (default width = 79):

```{r}
tula(m, wide = TRUE)
```

Wide (width = Inf):

```{r}
tula(m, wide = TRUE, width = Inf)
```

---

## 9 — `width` sweep: same model at several explicit widths

Shows the effect of varying `width` on a model with moderately long names.
Useful for calibrating what width feels right.

```{r}
#| echo: false
set.seed(1)
df9 <- data.frame(
  y               = rnorm(120, 50, 10),
  age             = sample(18:65, 120, replace = TRUE),
  years_of_formal_education_completed = sample(8:20, 120, replace = TRUE),
  employment_status = factor(sample(c(
    "Employed full-time",
    "Employed part-time",
    "Unemployed and seeking work",
    "Not in the labor force"
  ), 120, replace = TRUE))
)
m9 <- lm(y ~ age + years_of_formal_education_completed + employment_status,
         data = df9)
```

width = 60:

```{r}
tula(m9, width = 60)
```

width = 72:

```{r}
tula(m9, width = 72)
```

width = 79 (default):

```{r}
tula(m9)
```

width = 100:

```{r}
tula(m9, width = 100)
```

width = Inf (full natural width):

```{r}
tula(m9, width = Inf)
```

---

## 10 — `width` with `wide = TRUE`

Wide mode needs more horizontal space for CI columns, so the label column is
squeezed more aggressively at the same `width`.

wide = TRUE, width = 79 (default):

```{r}
tula(m9, wide = TRUE)
```

wide = TRUE, width = 100:

```{r}
tula(m9, wide = TRUE, width = 100)
```

wide = TRUE, width = 120:

```{r}
tula(m9, wide = TRUE, width = 120)
```

wide = TRUE, width = Inf:

```{r}
tula(m9, wide = TRUE, width = Inf)
```

---

## 11 — `width` below the minimum usable width

When `width` is set smaller than the space needed for the numeric columns
alone, the label column shrinks toward 1 character and everything gets
truncated to `~`.

```{r}
#| echo: false
m11 <- lm(mpg ~ factor(cyl) + wt, data = mtcars)
```

width = 79 (default):

```{r}
tula(m11)
```

width = 50:

```{r}
tula(m11, width = 50)
```

width = 42 (near the minimum for narrow mode):

```{r}
tula(m11, width = 42)
```
