---
title: "tula — Multinomial Logit Visual Tests"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
# Load the tula package from source.
# Run this script from the package directory, or set the path below.
library(nnet)
devtools::load_all(".")
```

---

# Basics

## Test 11 — basic three-outcome model

**Expected:** Shared header (AIC, BIC, Log likelihood / N, McFadden R-sq).
Two outcome blocks (`6`, `8`) each separated by a dashed line with the outcome
label between. `(Intercept)` at the bottom of each block. Footer: `Base outcome: 4`.

```{r}
#| echo: false
m11 <- multinom(factor(cyl) ~ wt + hp, data = mtcars, trace = FALSE)
```

Narrow:

```{r}
tula(m11)
```

Wide:

```{r}
tula(m11, wide = TRUE)
```

---

## Test 12 — factor predictor, grouping in each block

**Expected:** `am` appears as a grouped factor header with indented level `1`
in every outcome block — the same Stata-style grouping as lm/glm. Wide mode
adds CI columns to every block.

```{r}
#| echo: false
m12 <- multinom(factor(cyl) ~ wt + hp + factor(am), data = mtcars, trace = FALSE)
```

Narrow:

```{r}
tula(m12)
```

Wide:

```{r}
tula(m12, wide = TRUE)
```

---

## Test 13 — four-outcome model

**Expected:** Three outcome blocks (S, M, L with XS as base), each containing
a `Species` factor group and a `Sepal.Width` row. Header and footer correct.

```{r}
#| echo: false
iris4 <- iris
iris4$size <- cut(iris$Sepal.Length,
                  breaks = quantile(iris$Sepal.Length, c(0, .25, .5, .75, 1)),
                  labels = c("XS", "S", "M", "L"),
                  include.lowest = TRUE)
m13 <- multinom(size ~ Sepal.Width + Species, data = iris4, trace = FALSE)
```

```{r}
tula(m13)
```

---

## Test 14 — long outcome labels (truncation test)

**Expected:** Each outcome label appears on the same line as the column headers
(Coef., Std. Err., z, P>|z|), in the label-column area left of `|`. When an
outcome label is longer than the label column, it is truncated with `~` — the
`|` separator must remain perfectly aligned in every row of the output.
"Base outcome:" remains as a footer below the final separator.

```{r}
#| echo: false
set.seed(42)
df14 <- data.frame(
  outcome = factor(
    sample(c("Not in labor force", "Part-time employed", "Full-time employed"),
           size = 200, replace = TRUE, prob = c(0.3, 0.3, 0.4)),
    levels = c("Not in labor force", "Part-time employed", "Full-time employed")
  ),
  age    = rnorm(200, mean = 40, sd = 12),
  female = rbinom(200, size = 1, prob = 0.5)
)
m14 <- multinom(outcome ~ age + female, data = df14, trace = FALSE)
```

Default width:

```{r}
tula(m14)
```

wide = TRUE:

```{r}
tula(m14, wide = TRUE)
```

width = 68 (forces label truncation):

```{r}
tula(m14, width = 68)
```

---

## Test 15 — multinom vs glm on binary outcome (sanity check)

**Expected:** Coefficients, SEs, z-stats, and p-values from `multinom()` on a
two-level outcome should match those from `glm(..., family = binomial)` closely
(up to sign conventions — multinom models log-odds of level 2 vs level 1).

```{r}
#| echo: false
m15_glm <- glm(am ~ wt + hp, data = mtcars, family = binomial)
m15_mn  <- multinom(factor(am) ~ wt + hp, data = mtcars, trace = FALSE)
```

glm (logistic):

```{r}
tula(m15_glm)
```

multinom (binary):

```{r}
tula(m15_mn)
```

---

## Test 15b — binary multinom with factor predictor

**Expected:** Single outcome block (one non-base level). Factor grouping
(`cyl` header with indented levels) appears exactly as in lm/glm. Verifies
that factor handling works correctly even when the outcome is binary.

```{r}
#| echo: false
m15b <- multinom(factor(am) ~ wt + hp + factor(cyl), data = mtcars, trace = FALSE)
```

```{r}
tula(m15b)
```

---

# `ref = TRUE`

## Test 20 — `ref = TRUE`: multinom

**Expected:** Each factor group in every outcome block gets a reference row
appended after its non-reference levels. Numeric columns blank on that row.

```{r}
#| echo: false
m20 <- multinom(factor(cyl) ~ wt + hp + factor(am), data = mtcars, trace = FALSE)
```

ref = TRUE, narrow:

```{r}
tula(m20, ref = TRUE)
```

ref = TRUE, wide:

```{r}
tula(m20, ref = TRUE, wide = TRUE)
```

---

# `exp = TRUE`

## Test 28 — `exp = TRUE`: multinom

**Expected:** Each outcome block shows exponentiated coefficients and DMSE.
Column headers `exp(b)` and `DMSE` appear in every block. Footer unchanged.

```{r}
#| echo: false
m28 <- multinom(factor(cyl) ~ wt + hp, data = mtcars, trace = FALSE)
```

exp = FALSE:

```{r}
tula(m28)
```

exp = TRUE:

```{r}
tula(m28, exp = TRUE)
```

---

## Test 29 — `exp = TRUE`: multinom with factor and `ref = TRUE`

**Expected:** Reference rows in each outcome block show `1`. Factor headers
blank. Exponentiated coefficients and DMSE in all regular rows.

```{r}
#| echo: false
m29 <- multinom(factor(cyl) ~ wt + hp + factor(am), data = mtcars, trace = FALSE)
```

exp = TRUE, ref = TRUE:

```{r}
tula(m29, exp = TRUE, ref = TRUE)
```

---

# `wide` / `width` options

## Test 32 — `width` option forces label truncation

**Expected:** Long labels truncated with `~` in every outcome block; separators
and all rows the same width.

```{r}
#| echo: false
df32 <- mtcars
names(df32)[names(df32) == "wt"] <- "vehicle_weight_lbs"
names(df32)[names(df32) == "hp"] <- "gross_horsepower_bhp"
m32 <- multinom(factor(cyl) ~ vehicle_weight_lbs + gross_horsepower_bhp,
                data = df32, trace = FALSE)
```

Default width:

```{r}
tula(m32)
```

width = 68:

```{r}
tula(m32, width = 68)
```

---

## Test 33 — `width` below minimum (warning + clamp to 60)

**Expected:** A warning is issued ("width cannot be less than 60; using width = 60.")
and the output is produced at width = 60, not suppressed.

multinom with width = 30 (should warn and use 60):

```{r}
withCallingHandlers(
  tula(multinom(factor(cyl) ~ wt + hp, data = mtcars, trace = FALSE), width = 30),
  warning = function(w) { cat("Warning:", conditionMessage(w), "\n"); invokeRestart("muffleWarning") }
)
```

---

# `parallel = TRUE`

## Test 33a — parallel: basic layout (3-level outcome)

**Expected:** A single coefficient table with outcome category names as column
headers (right-aligned). Each predictor occupies two rows: estimate (with
significance stars) on top, SE in parentheses below. Factor group-header rows
span the full width with no numeric content. Intercept goes last after a
separator. `dep_var` label appears in the upper-left of the column header row.
Header block printed once above the table. "Base outcome:" and star legend
printed below.

```{r}
#| echo: false
m_par <- multinom(factor(cyl) ~ wt + hp, data = mtcars, trace = FALSE)
```

Stacked layout (default):

```{r}
tula(m_par)
```

Parallel layout:

```{r}
tula(m_par, parallel = TRUE)
```

---

## Test 33b — parallel: factor predictor, `ref = TRUE`, and `ref = FALSE`

**Expected:** Factor group-header rows print with label only, no numeric cells.
With `ref = FALSE` (default): reference level omitted, single indented level
row for each factor level. With `ref = TRUE`: reference level rows show `0`
(right-aligned) in each outcome column with blank SE rows.

```{r}
#| echo: false
mtcars$gear_f <- factor(mtcars$gear)
m_par2 <- multinom(factor(cyl) ~ wt + gear_f, data = mtcars, trace = FALSE)
```

parallel = TRUE (ref = FALSE, default):

```{r}
tula(m_par2, parallel = TRUE)
```

parallel = TRUE, ref = TRUE:

```{r}
tula(m_par2, parallel = TRUE, ref = TRUE)
```

---

## Test 33c — parallel: `exp = TRUE`

**Expected:** Estimate column shows `exp(b)`, SE column shows delta-method SE
`exp(b) * SE(b)`. Stars still appended based on the unchanged p-value.
Reference rows (if shown with `ref = TRUE`) display `1` instead of `0`, with
blank SE row. No confidence intervals.

parallel = TRUE, exp = TRUE:

```{r}
tula(m_par, parallel = TRUE, exp = TRUE)
```

parallel = TRUE, exp = TRUE, ref = TRUE:

```{r}
tula(m_par2, parallel = TRUE, exp = TRUE, ref = TRUE)
```

---

## Test 33d — parallel: many outcome columns; width-exceeded error

**Expected:** First call (default width = 80) succeeds and shows 5 outcome
columns for `carb`. Second call at `width = 60` triggers an informative error
noting that the combination of width and number of outcomes is too narrow, and
suggesting a larger `width` or `parallel = FALSE`.

```{r}
#| echo: false
m_carb <- multinom(factor(carb) ~ wt + hp, data = mtcars, trace = FALSE)
```

6-level carb model, parallel = TRUE, width = 80 (just fits):

```{r}
tula(m_carb, parallel = TRUE, width = 80)
```

Same model, width = 60 (should error --- 5 columns need all 60 chars):

```{r}
tryCatch(
  print(tula(m_carb, parallel = TRUE, width = 60)),
  error = function(e) cat("Error caught as expected:\n", conditionMessage(e), "\n")
)
```
