---
title: "tula — Multinomial Logit Output Exploration"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
library(nnet)
devtools::load_all(".")
set.seed(42)
```

This file tests `tula()` for `multinom` objects from `nnet::multinom()`.

---

## 1 — Basic three-outcome model (numeric predictors only)

Three cylinder levels in `mtcars`. Base outcome is 4 (the first level).

```{r basic}
m1 <- multinom(factor(cyl) ~ wt + hp, data = mtcars, trace = FALSE)
tula(m1)
```

---

## 2 — With a factor predictor

Tests that factor grouping (Stata-style header + indented levels) works
across all outcome blocks.

```{r factor-predictor}
m2 <- multinom(factor(cyl) ~ wt + hp + factor(am), data = mtcars, trace = FALSE)
tula(m2)
```

---

## 3 — ref = TRUE

Reference level row should appear within each factor group in every block.

```{r ref-true}
tula(m2, ref = TRUE)
```

---

## 4 — wide = TRUE (confidence intervals)

CI columns should appear in every outcome block.

```{r wide}
tula(m2, wide = TRUE)
```

---

## 5 — wide = TRUE and ref = TRUE together

```{r wide-ref}
tula(m2, wide = TRUE, ref = TRUE)
```

---

## 6 — Two-outcome model (binary, as a sanity check)

When only one non-base outcome exists the output should be a single block.

```{r binary}
m3 <- multinom(factor(am) ~ wt + hp + factor(cyl), data = mtcars, trace = FALSE)
tula(m3)
```

---

## 7 — Four-outcome model

Uses the `iris` species (three outcomes) and a continuous predictor.

```{r four-outcome}
# Create a four-level outcome for a more demanding test
iris4 <- iris
iris4$size <- cut(iris$Sepal.Length,
                  breaks = quantile(iris$Sepal.Length, c(0, .25, .5, .75, 1)),
                  labels = c("XS", "S", "M", "L"),
                  include.lowest = TRUE)
m4 <- multinom(size ~ Sepal.Width + Petal.Length + Species,
               data = iris4, trace = FALSE)
tula(m4)
```

---

## 8 — width option

Narrower width forces label truncation.

```{r width}
cat("width = 72:\n")
tula(m2, width = 72)
```

---

## 9 — Long predictor names

Tests label truncation in a multinomial context.

```{r long-names}
df_long <- mtcars
names(df_long)[which(names(df_long) == "wt")]  <- "vehicle_weight_lbs"
names(df_long)[which(names(df_long) == "hp")]  <- "gross_horsepower_bhp"
m5 <- multinom(factor(cyl) ~ vehicle_weight_lbs + gross_horsepower_bhp,
               data = df_long, trace = FALSE)
tula(m5)
```

---

## 10 — Comparison: glm on binary outcome vs multinom

Both should give identical (or near-identical) coefficients.

```{r compare}
# glm logistic
m_glm <- glm(am ~ wt + hp, data = mtcars, family = binomial)
cat("glm (logistic):\n")
tula(m_glm)

# multinom equivalent
m_mn <- multinom(factor(am) ~ wt + hp, data = mtcars, trace = FALSE)
cat("\nmultinom (binary):\n")
tula(m_mn)
```
