---
title: "tula — Negative Binomial Visual Tests"
format: html
execute:
  warning: false
  message: false
---

```{r setup}
library(MASS)
devtools::load_all(".")
```

# Basics

## Test 1 --- basic numeric predictors

**Expected:** Family label "Family: Negative Binomial / Link: log".
Header: AIC, BIC, Log likelihood (left), Number of obs, McFadden R-sq (right).
Coefficient table with z/P>|z|. Ancillary section at bottom with `/lnalpha`
and `alpha` rows, each preceded by a separator, with blank z and p columns.

```{r test1}
m1 <- glm.nb(carb ~ wt + hp, data = mtcars)
tula(m1)
```

---

## Test 2 --- wide mode (CIs on coefficients and ancillary)

**Expected:** 95% CI columns appear on both the main coefficient rows AND the
ancillary rows. The `alpha` CI should be asymmetric (exponential
back-transform of the `lnalpha` CI).

```{r test2}
tula(m1, wide = TRUE)
```

---

## Test 3 --- factor predictor

**Expected:** `cyl` appears as a grouped factor header with indented levels
`6` and `8` in the coefficient section. Ancillary section unchanged.

```{r test3}
m3 <- glm.nb(carb ~ wt + factor(cyl), data = mtcars)
tula(m3)
```

---

## Test 4 --- ref = TRUE

**Expected:** Reference level `4` appears as the last row within the `cyl`
factor group, with coefficient `0` and blank SE/z/p.

```{r test4}
tula(m3, ref = TRUE)
```

---

## Test 5 --- ref = TRUE, wide = TRUE

**Expected:** Reference level visible, CI columns on all rows including
ancillary. CIs for reference row are blank.

```{r test5}
tula(m3, ref = TRUE, wide = TRUE)
```

---

# exp = TRUE (IRR)

## Test 6 --- IRR column header

**Expected:** Column header reads `"IRR"` (not `"exp(b)"`). SE column reads
`"DMSE"`. Coefficients are exponentiated. Reference rows (if shown) display
`1`. Ancillary section (`/lnalpha` and `alpha`) is NOT exponentiated --- same
values as without `exp`. Message about CIs being suppressed.

```{r test6}
tula(m3, exp = TRUE, ref = TRUE)
```

---

## Test 7 --- exp = TRUE, wide = FALSE (no message)

**Expected:** No CI-suppression message when `wide = FALSE` is explicit.

```{r test7}
tula(m3, exp = TRUE, wide = FALSE)
```

---

# Width constraints

## Test 8 --- narrow width with label truncation

**Expected:** Long variable names are truncated with `~`. All rows (including
ancillary) have the same total width.

```{r test8}
df8 <- mtcars
df8$very_long_variable_name <- mtcars$hp
m8 <- glm.nb(carb ~ wt + very_long_variable_name + factor(cyl), data = df8)
tula(m8, width = 68)
```

---

## Test 9 --- comparison with Poisson glm on same data

**Expected:** Coefficient signs and rough magnitudes should be similar between
NB and Poisson on the same data. The NB model has an ancillary section; the
Poisson does not.

```{r test9}
cat("Negative binomial:\n")
tula(m1)
cat("\nPoisson:\n")
m_pois <- glm(carb ~ wt + hp, data = mtcars, family = poisson)
tula(m_pois)
```
