---
title: "tula — Ordered Regression Output Tests"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
library(MASS)
devtools::load_all(".")
set.seed(42)

# Shared data objects used across tests
mtcars$gear_ord <- factor(mtcars$gear, ordered = TRUE)   # 3 levels → 2 cutpoints

# Four-level ordered outcome on iris (150 obs — avoids separation on small mtcars)
iris4 <- iris
iris4$size <- cut(iris$Sepal.Length,
                  breaks = quantile(iris$Sepal.Length, c(0, .25, .5, .75, 1)),
                  labels = c("XS", "S", "M", "L"),
                  include.lowest = TRUE,
                  ordered_result = TRUE)
```

This file tests `tula()` for `polr` objects from `MASS::polr()` and,
conditionally, `clm` objects from `ordinal::clm()`.

---

# polr (MASS)

## 1 — Basic model, numeric predictors only

Simplest case: continuous predictors, three-level ordered outcome.
Two cutpoints should appear in the lower section, separated by a rule.
z and P>|z| columns for cutpoints should be **blank**.

```{r polr-basic}
m1 <- polr(gear_ord ~ mpg + wt, data = mtcars, Hess = TRUE)
tula(m1, width = 72)
```

---

## 2 — With a factor predictor

`factor(cyl)` should produce the Stata-style group header + indented levels
in the predictor section, while cutpoints remain in their own section below.

```{r polr-factor}
m2 <- polr(gear_ord ~ mpg + factor(cyl), data = mtcars, Hess = TRUE)
tula(m2, width = 72)
```

---

## 3 — ref = TRUE

Reference level row should appear inside the factor group.
Cutpoints section is unaffected.

```{r polr-ref}
tula(m2, ref = TRUE, width = 72)
```

---

## 4 — wide = TRUE (confidence intervals)

CI columns should appear for **both** predictor rows and cutpoint rows.
z and P>|z| columns for cutpoints should still be blank.

```{r polr-wide}
tula(m2, wide = TRUE, width = 100)
```

---

## 5 — wide = TRUE and ref = TRUE together

```{r polr-wide-ref}
tula(m2, wide = TRUE, ref = TRUE, width = 100)
```

---

## 6 — exp = TRUE (odds ratios)

Predictor rows: estimate column shows exp(b), SE column shows delta-method SE.
Cutpoint rows: **not** exponentiated (they are threshold parameters, not
log-odds coefficients), displayed as raw values.
A note about CIs being suppressed should appear.

```{r polr-exp}
tula(m2, exp = TRUE, width = 72)
```

---

## 7 — exp = TRUE with explicit wide = FALSE

No message should appear (user already opted out of CIs).

```{r polr-exp-no-msg}
tula(m2, exp = TRUE, wide = FALSE, width = 72)
```

---

## 8 — Four-level outcome (three cutpoints)

Uses `iris4` (150 obs) to avoid separation with `mtcars` (32 obs).
Three cutpoints (XS|S, S|M, M|L) should appear in the lower section.

```{r polr-four-level}
m3 <- polr(size ~ Sepal.Width + Petal.Length + Species, data = iris4, Hess = TRUE)
tula(m3, width = 72)
```

---

## 9 — Probit link

`model$method` is "probit"; family label line should reflect that.
Coefficients differ from logistic but layout is identical.

```{r polr-probit}
m4 <- polr(gear_ord ~ mpg + wt, data = mtcars, method = "probit", Hess = TRUE)
tula(m4, width = 72)
```

---

## 10 — Numeric predictors only (no factor), narrow width

Label column is minimal; verifies width calculation doesn't break.

```{r polr-narrow}
tula(m1, width = 65)
```

---

## 11 — Long predictor names (label truncation)

Labels exceeding the column width should be truncated with `~`.

```{r polr-long-names}
df_long <- mtcars
names(df_long)[names(df_long) == "mpg"] <- "miles_per_gallon_epa"
names(df_long)[names(df_long) == "wt"]  <- "vehicle_weight_thousands"
m5 <- polr(gear_ord ~ miles_per_gallon_epa + vehicle_weight_thousands,
           data = df_long, Hess = TRUE)
tula(m5, width = 72)
```

---

## 12 — All four polr link functions

Verifies that the family label changes correctly for each link.
The coefficient values will differ; the output structure should be identical.

```{r polr-links}
m_logistic <- polr(gear_ord ~ mpg + wt, data = mtcars, method = "logistic", Hess = TRUE)
m_probit   <- polr(gear_ord ~ mpg + wt, data = mtcars, method = "probit",   Hess = TRUE)
m_cloglog  <- polr(gear_ord ~ mpg + wt, data = mtcars, method = "cloglog",  Hess = TRUE)
m_cauchit  <- polr(gear_ord ~ mpg + wt, data = mtcars, method = "cauchit",  Hess = TRUE)

cat("logistic:\n");  tula(m_logistic, width = 72)
cat("\nprobit:\n");  tula(m_probit,   width = 72)
cat("\ncloglog:\n"); tula(m_cloglog,  width = 72)
cat("\ncauchit:\n"); tula(m_cauchit,  width = 72)
```

---

## 13 — width below minimum (warning + clamp to 60)

**Expected:** warning about width < 60, then output at width = 60.

```{r polr-width-min}
withCallingHandlers(
  tula(m1, width = 40),
  warning = function(w) {
    cat("Warning:", conditionMessage(w), "\n")
    invokeRestart("muffleWarning")
  }
)
```

---

# clm (ordinal)

```{r clm-check}
has_ordinal <- requireNamespace("ordinal", quietly = TRUE)
if (!has_ordinal) cat("ordinal package not installed — clm tests skipped.\n")
```

## 14 — Basic clm, numeric predictors

Results should be numerically close to the matching polr model (Test 1).
The family label should read "Ordered regression / Link: logit".

```{r clm-basic}
#| eval: !expr has_ordinal
library(ordinal)
mc1 <- clm(gear_ord ~ mpg + wt, data = mtcars)
tula(mc1, width = 72)
```

---

## 15 — clm with a factor predictor

Factor grouping should behave identically to polr.

```{r clm-factor}
#| eval: !expr has_ordinal
mc2 <- clm(gear_ord ~ mpg + factor(cyl), data = mtcars)
tula(mc2, width = 72)
```

---

## 16 — clm ref = TRUE

```{r clm-ref}
#| eval: !expr has_ordinal
tula(mc2, ref = TRUE, width = 72)
```

---

## 17 — clm wide = TRUE

CI columns for both predictors and cutpoints.

```{r clm-wide}
#| eval: !expr has_ordinal
tula(mc2, wide = TRUE, width = 100)
```

---

## 18 — clm probit link

```{r clm-probit}
#| eval: !expr has_ordinal
mc3 <- clm(gear_ord ~ mpg + wt, data = mtcars, link = "probit")
tula(mc3, width = 72)
```

---

## 19 — polr / clm coefficient agreement

Coefficients from polr and clm on the same data/formula should agree
closely (both fit the proportional-odds model; minor differences arise
from convergence tolerance and optimiser).

```{r polr-clm-agree}
#| eval: !expr has_ordinal
m_polr_cmp <- polr(gear_ord ~ mpg + factor(cyl), data = mtcars, Hess = TRUE)
cat("polr:\n")
tula(m_polr_cmp, width = 72)
cat("\nclm:\n")
tula(mc2, width = 72)
```
