---
title: "tula — Summarize Output Exploration"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
devtools::load_all(".")
set.seed(42)
```

This file tests `tula()` when called on data frames, tibbles, and vectors,
producing Stata-style `-summarize-` output.

---

## 1 — Numeric data frame (`mtcars`)

The simplest case: all numeric columns, default options (`sep = 5`).

```{r numeric-df}
tula(mtcars)
```

---

## 2 — Mixed types: numeric, factor, logical, character

Tests that each variable type is handled appropriately.

- **numeric**: full row (N, Mean, SD, Min, Max)
- **factor**: header row with N, then indented level rows with proportion
- **character**: N only, "(string)" in Mean column
- **logical**: treated as 0/1 integer

```{r mixed-types}
df_mixed <- data.frame(
  age            = c(25L, 30L, NA, 40L, 35L, 28L),
  sex            = factor(c("Male", "Female", "Male", "Female", "Male", "Female")),
  name           = c("Alice", "Bob", "Carol", "Dan", "Eve", "Frank"),
  active         = c(TRUE, FALSE, TRUE, NA, TRUE, FALSE),
  score          = c(82.5, 91.0, NA, 78.3, 95.1, 88.7),
  stringsAsFactors = FALSE
)
tula(df_mixed)
```

---

## 3 — Single numeric vector

Tests name capture: the variable name in the output should reflect what the
user typed.

```{r single-numeric}
mpg <- mtcars$mpg
tula(mpg)
```

```{r single-numeric-inline}
# Inline expression — deparse turns $ to .
tula(mtcars$wt)
```

---

## 4 — Single factor vector

Factor level proportions, single-variable case.

```{r single-factor}
cyl_f <- factor(mtcars$cyl)
tula(cyl_f)
```

```{r single-factor-labeled}
transmission <- factor(mtcars$am, labels = c("automatic", "manual"))
tula(transmission)
```

---

## 5 — Single logical vector

Should be treated as 0/1: mean = proportion TRUE among non-missing.

```{r single-logical}
passed <- c(TRUE, FALSE, TRUE, TRUE, NA, FALSE, TRUE)
tula(passed)
```

---

## 6 — Single character vector

Should show N and "(string)" in the Mean column; all other columns blank.

```{r single-character}
names_vec <- c("Alice", "Bob", NA, "Carol", "Dan")
tula(names_vec)
```

---

## 7 — `sep` option

The `sep` option controls how many variables appear between each dash-line
separator. `sep = 0` suppresses separators entirely.

```{r sep-0}
cat("sep = 0 (no separators):\n")
tula(mtcars, sep = 0)
```

```{r sep-3}
cat("sep = 3:\n")
tula(mtcars, sep = 3)
```

```{r sep-5}
cat("sep = 5 (default):\n")
tula(mtcars)
```

```{r sep-10}
cat("sep = 10 (more than all variables — no mid-table separators):\n")
tula(mtcars, sep = 10)
```

---

## 8 — `sep` with factor variables: boundary behaviour

Separators should never split a factor's level rows. If a sep boundary
falls on a factor variable, the separator goes *after* the factor block.

```{r sep-factor-boundary}
# cyl is at position 4, which is a sep=3 boundary.
# Separator should appear AFTER cyl's level rows, not before them.
df_sep <- data.frame(
  mpg   = mtcars$mpg,
  disp  = mtcars$disp,
  hp    = mtcars$hp,
  cyl_f = factor(mtcars$cyl),     # position 4 = sep boundary
  wt    = mtcars$wt,
  qsec  = mtcars$qsec
)
cat("sep = 3, factor at position 4:\n")
tula(df_sep, sep = 3)
```

---

## 9 — `mad = TRUE`

Replace standard deviation with mean absolute deviation; column header
changes to "MAD".

```{r mad-true}
cat("Default (Std. dev.):\n")
tula(mtcars[, c("mpg", "wt", "hp")])

cat("\nmad = TRUE (MAD):\n")
tula(mtcars[, c("mpg", "wt", "hp")], mad = TRUE)
```

---

## 10 — `median = TRUE`

Replace Mean with Median and SD with IQR; column headers change accordingly.

```{r median-true}
cat("Default (Mean / Std. dev.):\n")
tula(mtcars[, c("mpg", "wt", "hp")])

cat("\nmedian = TRUE (Median / IQR):\n")
tula(mtcars[, c("mpg", "wt", "hp")], median = TRUE)
```

---

## 11 — `median = TRUE` with factor variables

Factor display (proportions) should be unchanged when `median = TRUE`.

```{r median-factor}
df_med_fac <- data.frame(
  income    = c(45000, 80000, 120000, 60000, 95000, 72000),
  education = factor(c("HS", "College", "Graduate", "HS", "College", "Graduate")),
  age       = c(28, 35, 42, 31, 38, 45)
)
cat("median = TRUE with factor:\n")
tula(df_med_fac, median = TRUE)
```

---

## 12 — Long variable names and truncation

Long names are truncated using the same word-boundary `~` logic as in
regression output.

```{r long-names}
df_long <- data.frame(
  years_of_formal_education_completed = sample(8:20, 50, replace = TRUE),
  self_reported_annual_household_income = round(rnorm(50, 75000, 25000)),
  employment_status = factor(sample(
    c("Full-time employed", "Part-time employed", "Unemployed", "Not in labor force"),
    50, replace = TRUE
  )),
  age = sample(22:65, 50, replace = TRUE)
)

cat("Default width:\n")
tula(df_long)

cat("\nwidth = Inf (no truncation):\n")
tula(df_long, width = Inf)

cat("\nwidth = 70 (tighter):\n")
tula(df_long, width = 70)
```

---

## 13 — `width = Inf`

No truncation; output expands to natural width of the widest label.

```{r width-inf}
tula(mtcars, width = Inf)
```

---

## 14 — Single-column data frame

```{r single-col-df}
tula(data.frame(mpg = mtcars$mpg))
```

---

## 15 — Data frame with NAs throughout

Verifies that N counts non-missing correctly for each variable.

```{r nas}
df_na <- data.frame(
  x = c(1, NA, 3, NA, 5),
  y = c(NA, 2, NA, 4, NA),
  g = factor(c("a", NA, "b", "a", NA))
)
tula(df_na)
```

---

## 16 — All options combined: `median = TRUE`, `mad` ignored, long names, `sep = 3`

```{r all-options}
tula(df_long, median = TRUE, sep = 3)
```

---

## 17 — Tibble input (if available)

If the `tibble` package is installed, verify that a tibble is handled
identically to a data frame.

```{r tibble}
if (requireNamespace("tibble", quietly = TRUE)) {
  tb <- tibble::as_tibble(mtcars[, 1:4])
  cat("Tibble input:\n")
  tula(tb)
} else {
  cat("tibble package not available — skipping\n")
}
```

---

## 18 — Regression output still works

Confirm the summarize path didn't break the regression path.

```{r regression-check}
cat("lm:\n")
tula(lm(mpg ~ factor(cyl) + wt, data = mtcars))

cat("\nglm:\n")
tula(glm(am ~ cyl + wt, data = mtcars, family = binomial))
```

---

## 19 — Large sample size

Exercises large N counts, large continuous values (income, age), and many-level
factors. Also checks that decimal-place capping works as expected: e.g. a mean
income of ~75,000 should not trail with unnecessary zeros, and proportions for
each education level should show up to 3 decimal places.

```{r large-n}
n <- 50000L
df_large <- data.frame(
  age           = as.integer(round(rnorm(n, mean = 42, sd = 13))),
  annual_income = round(rlnorm(n, meanlog = log(62000), sdlog = 0.7)),
  hours_per_week = round(rnorm(n, mean = 38, sd = 9), 1),
  employed      = sample(c(TRUE, FALSE), n, replace = TRUE, prob = c(0.62, 0.38)),
  education     = factor(
    sample(
      c("Less than HS", "High school", "Some college",
        "Bachelor's", "Graduate"),
      n, replace = TRUE, prob = c(0.10, 0.28, 0.22, 0.25, 0.15)
    ),
    levels = c("Less than HS", "High school", "Some college",
               "Bachelor's", "Graduate")
  ),
  region        = factor(
    sample(c("Northeast", "Midwest", "South", "West"), n,
           replace = TRUE, prob = c(0.18, 0.22, 0.38, 0.22))
  )
)
tula(df_large)
```
