---
title: "tula.svyglm() — Survey GLM Tests"
format: html
---

```{r setup}
devtools::load_all(".")
library(survey)
data(api)
```

## 1. Gaussian (linear survey regression) — stratified design

```{r}
dstrat <- svydesign(id = ~1, strata = ~stype, weights = ~pw, data = apistrat)
m1 <- svyglm(api00 ~ ell + meals + col.grad, design = dstrat)
summary(m1)
tula(m1)
```

## 2. Gaussian — wide (with CIs)

```{r}
tula(m1, wide = TRUE)
```

## 3. Gaussian — clustered design

```{r}
dclus <- svydesign(id = ~dnum, weights = ~pw, data = apiclus1)
m2 <- svyglm(api00 ~ ell + meals, design = dclus)
summary(m2)
tula(m2)
```

## 4. Logistic (quasibinomial) survey regression

```{r}
m3 <- svyglm(I(api00 > 700) ~ ell + meals, design = dstrat,
             family = quasibinomial())
summary(m3)
tula(m3)
```

## 5. Logistic with exp = TRUE (Odds Ratios)

```{r}
tula(m3, exp = TRUE)
```

## 6. Logistic with exp = TRUE and wide = TRUE

```{r}
tula(m3, exp = TRUE, wide = TRUE)
```

## 7. Poisson (quasipoisson) survey regression

```{r}
# Create a count-like variable for testing
apistrat$ell_cat <- as.integer(cut(apistrat$ell, breaks = c(-1, 10, 30, 50, 100)))
dstrat2 <- svydesign(id = ~1, strata = ~stype, weights = ~pw, data = apistrat)
m4 <- svyglm(ell_cat ~ meals + col.grad, design = dstrat2,
             family = quasipoisson())
summary(m4)
tula(m4)
```

## 8. Poisson with exp = TRUE (IRR)

```{r}
tula(m4, exp = TRUE)
```

## 9. Factor variables with ref = TRUE

```{r}
m5 <- svyglm(api00 ~ stype + meals, design = dstrat)
summary(m5)
tula(m5, ref = TRUE)
```

## 10. Warning when robust = TRUE

```{r}
tula(m1, robust = TRUE)
```

## 11. Different CI levels

```{r}
tula(m1, wide = TRUE, level = 90)
```

## 12. Comparison: regular glm vs survey glm

```{r}
cat("--- Regular GLM ---\n")
m_reg <- glm(api00 ~ ell + meals, data = apistrat)
tula(m_reg)

cat("\n--- Survey GLM (same data, stratified design) ---\n")
tula(m1)
```
