---
title: "tula.survreg() — Tobit / Survival Regression Tests"
format: html
---

```{r setup}
devtools::load_all(".")
library(AER)
library(survival)
data(Affairs, package = "AER")
```

## Test 1 — Basic tobit (AER Affairs data)

Matches the user's Stata example: `tobit affairs age yearsmarried religiousness rating, ll(0)`

```{r}
#| echo: false
m1 <- tobit(affairs ~ age + yearsmarried + religiousness + rating, data = Affairs)
```

`summary()`:

```{r}
summary(m1)
```

`tula()`:

```{r}
tula(m1)
```

## Test 2 — Factor variable

```{r}
#| echo: false
m2 <- tobit(affairs ~ factor(children) + age + yearsmarried, data = Affairs)
```

`summary()`:

```{r}
summary(m2)
```

`tula()`:

```{r}
tula(m2)
```

## Test 3 — wide = FALSE (narrow output)

`tula(wide = FALSE)`:

```{r}
tula(m1, wide = FALSE)
```

## Test 4 — robust = TRUE

Uses sandwich::sandwich() fallback since vcovHC() does not support survreg.

`tula(robust = TRUE)`:

```{r}
tula(m1, robust = TRUE)
```

## Test 5 — ref = TRUE

Shows reference level for factor variable.

`tula(ref = TRUE)`:

```{r}
tula(m2, ref = TRUE)
```

## Test 6 — exp = TRUE

Exponentiated coefficients (less common for tobit, but should work).

`tula(exp = TRUE)`:

```{r}
tula(m1, exp = TRUE)
```

## Test 7 — Bare survreg (Weibull, ovarian data)

Tests the non-tobit code path with a different distribution.

```{r}
#| echo: false
m_sv <- survreg(Surv(futime, fustat) ~ ecog.ps + rx + age,
                data = ovarian, dist = "weibull")
```

`summary()`:

```{r}
summary(m_sv)
```

`tula()`:

```{r}
tula(m_sv)
```

## Test 8 — Exponential distribution (no Log(scale) row)

Exponential has a fixed scale = 1, so no `/sigma` ancillary row should appear.

```{r}
#| echo: false
m_exp <- survreg(Surv(futime, fustat) ~ ecog.ps + rx + age,
                 data = ovarian, dist = "exponential")
```

`summary()`:

```{r}
summary(m_exp)
```

`tula()`:

```{r}
tula(m_exp)
```

## Test 9 — Right-censored tobit

```{r}
#| echo: false
m_right <- tobit(affairs ~ age + yearsmarried + religiousness + rating,
                 data = Affairs, left = -Inf, right = 12)
```

`tula()`:

```{r}
tula(m_right)
```

## Test 10 — Both-limits (interval) tobit

Shows Uncensored, Left-censored, and Right-censored counts in header.

```{r}
#| echo: false
m_both <- tobit(affairs ~ age + yearsmarried + religiousness + rating,
                data = Affairs, left = 0, right = 12)
```

`tula()`:

```{r}
tula(m_both)
```

## Test 11 — Interval regression (Affairs data, Surv type = "interval2")

Left-censored at 0 (affairs reported as 0) and interval-censored for positive
values (reported in a band). Uses `survreg` directly with `dist = "gaussian"`.

```{r}
#| echo: false
d <- Affairs
d$lo <- ifelse(d$affairs == 0, -Inf, d$affairs - 0.5)
d$hi <- ifelse(d$affairs == 0, 0, d$affairs + 0.5)

m_int <- survreg(Surv(lo, hi, type = "interval2") ~ age + yearsmarried +
                   religiousness + rating,
                 data = d, dist = "gaussian")
```

`summary()`:

```{r}
summary(m_int)
```

`tula()`:

```{r}
tula(m_int)
```

## Test 12 — Pure interval-censored data (simulated)

Every observation is interval-censored (observed in a unit-width band around
the true value). No left- or right-censored observations.

```{r}
#| echo: false
set.seed(42)
n <- 200
x1 <- rnorm(n)
x2 <- rnorm(n)
y_true <- 5 + 2 * x1 - 1.5 * x2 + rnorm(n, sd = 2)
lo2 <- floor(y_true)
hi2 <- lo2 + 1

m_int2 <- survreg(Surv(lo2, hi2, type = "interval2") ~ x1 + x2,
                  dist = "gaussian")
```

`summary()`:

```{r}
summary(m_int2)
```

`tula()`:

```{r}
tula(m_int2)
```

## Test 13 — Existing tula(lm) still works

Backward compatibility check.

```{r}
#| echo: false
m_lm <- lm(mpg ~ wt, data = mtcars)
```

`tula(lm)`:

```{r}
tula(m_lm)
```
