---
title: "The Tulaverse: Stata-Inspired Output in R"
format: html
---

The **tulaverse** package brings clean, readable console output to R.
One function call gives you formatted regression tables, descriptive
statistics, frequency tabulations, and more.

## Installation

```{r}
#| eval: false
# install.packages("remotes")
remotes::install_github("jeremyfreese/tulaverse")
```

```{r}
#| include: false
library(tulaverse)
library(haven)
library(nnet)

gss_full <- read_dta("/Users/jeremyfreese/Library/CloudStorage/Dropbox/GSS/gss7224_r2.dta")

gss <- gss_full[gss_full$year == 2024,
  c("age", "sex", "race", "educ", "degree", "realrinc",
    "happy", "health", "marital", "polviews", "partyid",
    "attend", "childs", "hrs1")]

gss$very_happy <- as.numeric(gss$happy == 1)
```

# tula()

The examples below use an extract from the 2024 General Social Survey ---
a nationally representative survey of American adults conducted since 1972.

## Descriptive statistics

One function call produces a clean, readable summary of every variable in a
data frame:

```{r}
tula(gss)
```

## Codebook

For a deeper look at each variable --- type, range, missingness, and either
a frequency tabulation or percentile summary --- add `codebook = TRUE`:

```{r}
tula(gss[, c("happy", "polviews", "educ", "realrinc")], codebook = TRUE)
```

## OLS regression

`tula()` wraps any fitted model in formatted output --- a header block with
fit statistics and a clean coefficient table:

```{r}
m_ols <- lm(realrinc ~ educ + age + sex + race, data = gss)
tula(m_ols)
```

## Display options

Add confidence intervals with `wide = TRUE`, show reference levels for factor
variables with `ref = TRUE`, and adjust the confidence level with `level`:

```{r}
tula(m_ols, wide = TRUE, ref = TRUE, level = 90)
```

## Robust standard errors

Heteroskedasticity-robust standard errors are one argument away. The column
header updates automatically:

```{r}
tula(m_ols, robust = TRUE)
```

## Logistic regression

Here we predict whether respondents report being "very happy" (vs. pretty
happy or not too happy):

```{r}
m_logit <- glm(very_happy ~ educ + age + health + marital,
               data = gss, family = binomial)
tula(m_logit)
```

Add `exp = TRUE` to see odds ratios instead of log-odds:

```{r}
tula(m_logit, exp = TRUE, wide = TRUE)
```

## Multinomial logit

For outcomes with more than two categories, `tula()` handles multinomial
logit via `nnet::multinom()`. Here we model the three-category happiness
variable directly:

```{r}
#| message: false
m_mlogit <- multinom(happy ~ educ + age + health, data = gss)
tula(m_mlogit)
```

With `parallel = TRUE`, the outcome categories are displayed side by side
with significance stars --- a compact view for comparing coefficients
across outcomes:

```{r}
tula(m_mlogit, parallel = TRUE)
```

# tulatab()

## Frequency tables

`tulatab()` produces frequency tables with haven value labels displayed
automatically:

```{r}
tulatab(polviews, data = gss)
```

## Crosstabulations

Pass two variables to get a two-way table with column percentages (use
`pct = "row"` or `pct = "cell"` for alternative layouts):

```{r}
tulatab(happy, degree, data = gss)
```

## Mean crosstab

Replace cell frequencies with means of a numeric variable using `mean =`:

```{r}
tulatab(degree, sex, data = gss, mean = realrinc)
```

# tulaplot()

## Visualization

`tulaplot()` is a thin wrapper around `ggplot()` that applies a clean theme
with larger text and sensible defaults:

```{r}
#| fig-width: 7
#| fig-height: 5
tulaplot(gss, ggplot2::aes(x = educ, y = realrinc)) +
  ggplot2::geom_point(alpha = 0.3) +
  ggplot2::geom_smooth(method = "lm", se = FALSE) +
  ggplot2::labs(x = "Years of education", y = "Income (constant $)",
                title = "Education and income, GSS 2024")
```

Use `scale_fill_tula()` for a matching color palette:

```{r}
#| fig-width: 7
#| fig-height: 5
tulaplot(gss[!is.na(gss$degree) & !is.na(gss$happy), ],
         ggplot2::aes(x = as_factor(degree), fill = as_factor(happy))) +
  ggplot2::geom_bar(position = "fill") +
  scale_fill_tula() +
  ggplot2::labs(x = "Highest degree", y = "Proportion", fill = "Happiness",
                title = "Happiness by education level, GSS 2024") +
  ggplot2::scale_y_continuous(labels = scales::percent)
```

# What else?

The tulaverse supports many more model types out of the box:

- **Negative binomial** (`MASS::glm.nb`)
- **Ordered logit/probit** (`MASS::polr`, `ordinal::clm`)
- **Cox proportional hazards** (`survival::coxph`)
- **Quantile regression** (`quantreg::rq`)
- **Fixed effects models** (`fixest::feols`, `feglm`, `fepois`, `fenegbin`)
- **Tobit / survival regression** (`AER::tobit`, `survival::survreg`)

Each one uses the same `tula()` call and supports the same display options
(`wide`, `ref`, `exp`, `robust`, `level`, and more).
