---
title: "The Tulaverse: Stata-Inspired Output in R"
format: html
---

The **tulaverse** package brings clean, readable console output to R.
One function call gives you formatted regression tables, descriptive
statistics, frequency tabulations, and more.

## Installation

```{r}
#| eval: false
# install.packages("remotes")
remotes::install_github("jeremyfreese/tulaverse")
```

```{r}
#| include: false
library(tulaverse)
library(haven)
library(nnet)

# Path to the GSS cumulative .dta file. Override by setting the
# TULAVERSE_GSS environment variable (e.g. in ~/.Renviron) or by
# editing the default below to match your local copy.
gss_path <- Sys.getenv(
  "TULAVERSE_GSS",
  unset = "~/Dropbox/GSS/gss7224_r2.dta"
)
gss_path <- path.expand(gss_path)

if (!file.exists(gss_path)) {
  stop(
    "GSS .dta file not found at '", gss_path, "'.\n",
    "Set the TULAVERSE_GSS environment variable to its location, ",
    "or edit gss_path in this chunk.",
    call. = FALSE
  )
}

gss_full <- read_dta(gss_path)

gss <- gss_full[gss_full$year == 2024,
  c("age", "sex", "race", "educ", "degree", "realrinc",
    "happy", "health", "marital", "polviews", "partyid",
    "attend", "childs", "hrs1")]

gss$very_happy <- as.numeric(gss$happy == 1)
```

# tula()

The examples below use an extract from the 2024 General Social Survey ---
a nationally representative survey of American adults conducted since 1972.

## Descriptive statistics

One function call produces a clean, readable summary of every variable in a
data frame:

```{r}
tula(gss)
```

## Codebook

For a deeper look at each variable --- type, range, missingness, and either
a frequency tabulation or percentile summary --- add `codebook = TRUE`:

```{r}
tula(gss[, c("happy", "polviews", "educ", "realrinc")], codebook = TRUE)
```

## OLS regression

`tula()` wraps any fitted model in formatted output --- a header block with
fit statistics and a clean coefficient table:

```{r}
m_ols <- lm(realrinc ~ educ + age + sex + race, data = gss)
tula(m_ols)
```

## Display options

Add confidence intervals with `wide = TRUE`, show reference levels for factor
variables with `ref = TRUE`, and adjust the confidence level with `level`:

```{r}
tula(m_ols, wide = TRUE, ref = TRUE, level = 90)
```

## Robust standard errors

Heteroskedasticity-robust standard errors are one argument away. The column
header updates automatically:

```{r}
tula(m_ols, robust = TRUE)
```

## Logistic regression

Here we predict whether respondents report being "very happy" (vs. pretty
happy or not too happy):

```{r}
m_logit <- glm(very_happy ~ educ + age + health + marital,
               data = gss, family = binomial)
tula(m_logit)
```

Add `exp = TRUE` to see odds ratios instead of log-odds:

```{r}
tula(m_logit, exp = TRUE, wide = TRUE)
```

## Multinomial logit

For outcomes with more than two categories, `tula()` handles multinomial
logit via `nnet::multinom()`. Here we model the three-category happiness
variable directly:

```{r}
#| message: false
m_mlogit <- multinom(happy ~ educ + age + health, data = gss)
tula(m_mlogit)
```

With `parallel = TRUE`, the outcome categories are displayed side by side
with significance stars --- a compact view for comparing coefficients
across outcomes:

```{r}
tula(m_mlogit, parallel = TRUE)
```

## Ordered logit

For ordered outcomes, `tula()` handles both `MASS::polr()` and
`ordinal::clm()`. Cutpoints appear in the footer:

```{r}
#| message: false
m_oprobit <- MASS::polr(as_factor(happy) ~ educ + age + health,
                        data = gss, method = "probit", Hess = TRUE)
tula(m_oprobit)
```

## Count outcomes

Negative binomial regression via `MASS::glm.nb()`:

```{r}
#| message: false
m_nb <- MASS::glm.nb(childs ~ educ + age + sex, data = gss)
tula(m_nb)
```

## Quantile regression

Pass a single `tau` or a vector of quantiles to `quantreg::rq()`. With
multiple quantiles, `parallel = TRUE` shows them side by side:

```{r}
#| message: false
m_rq <- quantreg::rq(realrinc ~ educ + age + sex,
                     tau = c(0.25, 0.5, 0.75), data = gss)
tula(m_rq, parallel = TRUE)
```

## Cox proportional hazards

For time-to-event outcomes, `tula()` handles `survival::coxph()`. The
`exp` argument defaults to `TRUE` for Cox models, so coefficients
print as hazard ratios:

```{r}
#| message: false
# Synthetic example using GSS age as "time" and very_happy as the event
m_cox <- survival::coxph(
  survival::Surv(age, very_happy) ~ educ + sex + health,
  data = gss
)
tula(m_cox)
```

## Conditional logit

For matched / choice-set data, `tula()` handles `survival::clogit()` with a
Stata-style "Conditional (fixed-effects) logistic regression" header (LR
chi2, Pseudo R2, number of strata):

```{r}
#| message: false
data(infert, package = "survival")
m_clogit <- survival::clogit(
  case ~ spontaneous + induced + strata(stratum),
  data = infert
)
tula(m_clogit, exp = TRUE, wide = TRUE)
```

## Tobit / survival regression

`tula()` handles both `AER::tobit()` (the typical tobit interface) and
`survival::survreg()` directly:

```{r}
#| message: false
m_tobit <- AER::tobit(realrinc ~ educ + age + sex, data = gss, left = 0)
tula(m_tobit)
```

## Fixed effects

`fixest` models pick up cluster-robust SEs by default and `tula()`
preserves the fixed effects panel in the header:

```{r}
#| message: false
m_fe <- fixest::feols(realrinc ~ educ + age + sex | race, data = gss)
tula(m_fe)
```

## Survey-weighted regression

When you have complex survey designs, fit with `survey::svyglm()`. The
design-based standard errors flow through automatically:

```{r}
#| message: false
des <- survey::svydesign(ids = ~1, weights = ~1, data = na.omit(
  gss[, c("realrinc", "educ", "age", "sex")]
))
m_svy <- survey::svyglm(realrinc ~ educ + age + sex, design = des)
tula(m_svy)
```

## Selecting coefficients

For long coefficient tables, `select =` prints just the rows you ask for.
Pass a factor's base name to grab the whole block:

```{r}
tula(m_ols, select = c("educ", "race"))
```

Add `selectheader = TRUE` or `selectfooter = TRUE` to bring back the
header or trailing rows.

# tulatab()

## Frequency tables

`tulatab()` produces frequency tables with haven value labels displayed
automatically:

```{r}
tulatab(polviews, data = gss)
```

## Crosstabulations

Pass two variables to get a two-way table with column percentages (use
`pct = "row"` or `pct = "cell"` for alternative layouts):

```{r}
tulatab(happy, degree, data = gss)
```

## Mean crosstab

Replace cell frequencies with means of a numeric variable using `mean =`:

```{r}
tulatab(degree, sex, data = gss, mean = realrinc)
```

## Multiple means in one table

In one-way mode, `mean = c(...)` shows several variables side by side
(or use `var =` as a synonym):

```{r}
tulatab(degree, data = gss, mean = c(realrinc, educ, hrs1))
```

## Custom summary statistics

The `stat =` argument replaces the default Mean + N columns with any
combination of `mean`, `median`, `sd`, `n`, and percentiles (`p1`--`p99`):

```{r}
tulatab(degree, data = gss, var = realrinc,
        stat = "median p25 p75 n")
```

## Crosstabs by panel

A `by =` variable produces one crosstab per panel:

```{r}
tulatab(happy, degree, data = gss, by = sex)
```

# tulaplot()

## Visualization

`tulaplot()` is a thin wrapper around `ggplot()` that applies a clean theme
with larger text and sensible defaults:

```{r}
#| fig-width: 7
#| fig-height: 5
tulaplot(gss, ggplot2::aes(x = educ, y = realrinc)) +
  ggplot2::geom_point(alpha = 0.3) +
  ggplot2::geom_smooth(method = "lm", se = FALSE) +
  ggplot2::labs(x = "Years of education", y = "Income (constant $)",
                title = "Education and income, GSS 2024")
```

Use `scale_fill_tula()` for a matching color palette:

```{r}
#| fig-width: 7
#| fig-height: 5
tulaplot(gss[!is.na(gss$degree) & !is.na(gss$happy), ],
         ggplot2::aes(x = as_factor(degree), fill = as_factor(happy))) +
  ggplot2::geom_bar(position = "fill") +
  scale_fill_tula() +
  ggplot2::labs(x = "Highest degree", y = "Proportion", fill = "Happiness",
                title = "Happiness by education level, GSS 2024") +
  ggplot2::scale_y_continuous(labels = scales::percent)
```

# What else?

A few other model types not shown above:

- **Ordered logit via `ordinal::clm()`** --- same `tula()` call as `polr`.
- **Other `fixest` families** --- `feglm`, `fepois`, `fenegbin`.
- **Survival regression via `survival::survreg()`** --- same path as
  `AER::tobit()`.
- **Constrained estimation via `restriktor::restriktor()`** --- header
  reports the constrained log-likelihood and original-model fit.

Each one uses the same `tula()` call and supports the same display options
(`wide`, `ref`, `exp`, `robust`, `level`, `select`, and more).
