---
title: "tulatab — Visual Test Script"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: true
---

```{r setup}
devtools::load_all(".")
set.seed(42)
```

# Basic variable types

## Test 1 — Ordered factor with Cum column

**Expected:** Frequency table with Cum column (ordered factor shows cumulative
percentages). Rows in level order. Percentages show exactly 2 decimal places.

```{r}
satisfaction <- ordered(
  sample(c("Low", "Medium", "High"), 200, replace = TRUE,
         prob = c(0.3, 0.5, 0.2)),
  levels = c("Low", "Medium", "High")
)
tulatab(satisfaction)
```

## Test 2 — Unordered factor without Cum column

**Expected:** Frequency table WITHOUT Cum column (unordered factor). Rows in
level order.

```{r}
colors <- factor(
  sample(c("red", "green", "blue"), 150, replace = TRUE),
  levels = c("red", "green", "blue")
)
tulatab(colors)
```

## Test 3 — Character variable without Cum column

**Expected:** Frequency table WITHOUT Cum column. Rows in alphabetical order.

```{r}
fruits <- sample(c("apple", "banana", "cherry", "date"), 100, replace = TRUE)
tulatab(fruits)
```

## Test 4 — Numeric variable with Cum column

**Expected:** Frequency table with Cum column. Values in ascending numeric
order. Comma-formatted counts.

```{r}
tulatab(mtcars$cyl)
```

# Missing values

## Test 5 — missing = TRUE with regular NAs

**Expected:** NA row(s) appear at the bottom of the table, labelled ".".
Percentages include NAs in the denominator and still sum to 100%.

```{r}
x_with_na <- c(rep("cat", 30), rep("dog", 45), rep("bird", 20), rep(NA, 5))
tulatab(x_with_na, missing = TRUE)
```

## Test 6 — missing = FALSE (default) excludes NAs

**Expected:** Same data as Test 5 but no NA row. Denominator excludes NAs.

```{r}
tulatab(x_with_na, missing = FALSE)
```

# Sorting

## Test 7 — sort = TRUE (descending frequency)

**Expected:** Rows sorted by descending frequency. Missing rows (if any)
always at bottom regardless of sort.

```{r}
x_sort <- c(rep("rare", 5), rep("common", 80), rep("medium", 30), rep(NA, 3))
tulatab(x_sort, sort = TRUE, missing = TRUE)
```

# Haven-labelled variables

## Test 8 — Haven-labelled variable (value=TRUE, label=TRUE)

**Expected:** Display shows both numeric code and label text separated by
whitespace (e.g. "1 Strong Democrat"). Cum column shown. Values in ascending
numeric order.

```{r}
library(haven)

party <- labelled(
  c(1, 1, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 4, 4, 5, 5, 5, 6, 6, 7),
  labels = c(
    "Strong Democrat"   = 1,
    "Not str Democrat"  = 2,
    "Ind, lean Dem"     = 3,
    "Independent"       = 4,
    "Ind, lean Rep"     = 5,
    "Not str Republican" = 6,
    "Strong Republican"  = 7
  ),
  label = "Party Identification"
)
tulatab(party)
```

## Test 9 — Haven-labelled with value=FALSE, label=TRUE

**Expected:** Only label text shown, no numeric codes. Same data as Test 8.

```{r}
tulatab(party, value = FALSE, label = TRUE)
```

## Test 10 — Haven-labelled with value=TRUE, label=FALSE

**Expected:** Only numeric codes shown, no label text.

```{r}
tulatab(party, value = TRUE, label = FALSE)
```

## Test 11 — Haven-labelled with value=FALSE, label=FALSE

**Expected:** Falls back to showing just numeric codes (same as value=TRUE,
label=FALSE).

```{r}
tulatab(party, value = FALSE, label = FALSE)
```

## Test 12 — Haven variable label in header

**Expected:** The variable label "Party Identification" appears in the
table header (left of the pipe), not the R variable name.

```{r}
tulatab(party)
```

## Test 13 — Haven tagged NAs

**Expected:** Each tagged NA gets its own row at the bottom with its label.

```{r}
tagged_vec <- labelled(
  c(1, 1, 2, 2, 3, tagged_na("a"), tagged_na("a"), tagged_na("b")),
  labels = c(
    "Yes"       = 1,
    "No"        = 2,
    "Maybe"     = 3,
    "Refused"   = tagged_na("a"),
    "Don't know" = tagged_na("b")
  ),
  label = "Response"
)
tulatab(tagged_vec, missing = TRUE)
```

# Calling conventions and width

## Test 14 — NSE data= calling convention

**Expected:** Works the same as direct vector, with the variable name
shown in the header.

```{r}
df_test <- data.frame(gear = mtcars$gear)
tulatab(gear, data = df_test)
```

## Test 15 — Width truncation

**Expected:** Labels truncated with ~ when output width is narrow.

```{r}
long_labels <- factor(c(
  rep("This is a very long category label that should be truncated", 30),
  rep("Another extremely long label for testing truncation behavior", 20),
  rep("Short", 50)
))
tulatab(long_labels, width = 60)
```

## Test 16 — Numeric with many unique values

**Expected:** Each unique value gets its own row. Cum column shown.
Values in ascending order.

```{r}
tulatab(mtcars$mpg)
```

## Test 17 — One-way mean= with numeric row variable (NSE)

**Expected:** Mean and N columns replace Freq/Percent/Cum.
Shows mean mpg for each cyl value (4, 6, 8) plus Total row.

```{r}
tulatab(cyl, data = mtcars, mean = mpg)
```

## Test 18 — One-way mean= with factor row variable

**Expected:** Factor levels shown with mean mpg and N per level.

```{r}
tulatab(factor(mtcars$cyl), mean = mtcars$mpg)
```

## Test 19 — One-way mean= with direct vectors

**Expected:** Same as Test 17 but using direct vector syntax.

```{r}
tulatab(mtcars$cyl, mean = mtcars$mpg)
```

## Test 20 — One-way mean= with sort=TRUE

**Expected:** Rows sorted by descending frequency. Mean and N columns.

```{r}
tulatab(cyl, data = mtcars, mean = mpg, sort = TRUE)
```

## Test 21 — One-way mean= with NAs in mean variable

**Expected:** N reflects non-missing count of mpg only.
Some rows may have reduced N.

```{r}
mtcars_na <- mtcars
mtcars_na$mpg[c(1, 5, 10, 15, 20)] <- NA
tulatab(cyl, data = mtcars_na, mean = mpg)
```

## Test 22 — One-way mean= with character row variable

**Expected:** Character categories with mean and N columns.

```{r}
colors <- c(rep("red", 10), rep("blue", 15), rep("green", 5))
vals   <- c(rnorm(10, 5), rnorm(15, 10), rnorm(5, 7))
set.seed(42)
vals   <- round(c(rnorm(10, 5), rnorm(15, 10), rnorm(5, 7)), 2)
tulatab(colors, mean = vals)
```

## Test 23 — One-way mean= with missing=TRUE

**Expected:** Includes NA row with its own mean and N.

```{r}
x_miss <- c(1, 1, 2, 2, 3, 3, NA, NA)
m_miss <- c(10, 20, 30, 40, 50, 60, 70, 80)
tulatab(x_miss, mean = m_miss, missing = TRUE)
```

## Test 24 — One-way mean= non-numeric error

**Expected:** Error message about mean variable must be numeric.

```{r, error=TRUE}
tulatab(cyl, data = mtcars, mean = gear > 3)
```

## Test 25 — One-way mean= length mismatch error

**Expected:** Error about length mismatch.

```{r, error=TRUE}
tulatab(mtcars$cyl, mean = 1:10)
```
