---
title: "tulaplot() visual tests"
format: html
---

```{r setup}
devtools::load_all(".")
library(ggplot2)
```

## 1. Basic scatterplot — verify background, grid, axis lines, text sizes

```{r}
tulaplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(title = "Weight vs MPG", subtitle = "Basic tulaplot test",
       x = "Weight (1000 lbs)", y = "Miles per gallon")
```

## 2. Color scale — `scale_color_tula()` with Stata 18 stcolor palette

```{r}
tulaplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  scale_color_tula() +
  labs(title = "Colored by cylinders", color = "Cylinders")
```

## 3. Fill scale — `scale_fill_tula()` with bar chart

```{r}
tulaplot(mtcars, aes(x = factor(cyl), fill = factor(gear))) +
  geom_bar(position = "dodge") +
  scale_fill_tula() +
  labs(title = "Cylinders by gear count", x = "Cylinders", fill = "Gears")
```

## 4. Faceted plot — verify strip background and text

```{r}
tulaplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  facet_wrap(~ cyl) +
  labs(title = "Faceted by cylinders")
```

## 5. Standalone `theme_tula()` — should look identical to tulaplot()

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  theme_tula() +
  labs(title = "Using theme_tula() standalone")
```

## 6. Custom `base_size = 18` — verify proportional scaling

```{r}
tulaplot(mtcars, aes(x = wt, y = mpg), base_size = 18) +
  geom_point() +
  labs(title = "Larger base size (18pt)")
```

## 7. 15+ levels — verify recycling warning

```{r}
df16 <- data.frame(
  x = 1:16, y = 1:16,
  grp = factor(paste0("G", sprintf("%02d", 1:16)))
)
tulaplot(df16, aes(x = x, y = y, color = grp)) +
  geom_point(size = 4) +
  scale_color_tula() +
  labs(title = "16 levels: should warn about recycling")
```

## 8. User override — confirm silent override (no warning messages)

```{r}
tulaplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  theme(panel.background = element_rect(fill = "lightyellow")) +
  labs(title = "User override: lightyellow background (no warnings)")
```

## 9. Line plot — single series (should be stc1 blue)

```{r}
tulaplot(economics, aes(x = date, y = unemploy / 1000)) +
  geom_line() +
  labs(title = "US unemployment over time",
       x = "Date", y = "Unemployed (millions)")
```

## 10. Line plot — multiple series with color

```{r}
library(tidyr)
library(dplyr)
econ_long <- economics |>
  mutate(unemp_rate = unemploy / pop * 100,
         save_rate  = psavert) |>
  select(date, unemp_rate, save_rate) |>
  pivot_longer(-date, names_to = "series", values_to = "value")

tulaplot(econ_long, aes(x = date, y = value, color = series)) +
  geom_line() +
  scale_color_tula() +
  labs(title = "Two time series", x = "Date", y = "Percent",
       color = "Series")
```

## 11. Histogram — single variable (should be stc1 blue fill)

```{r}
tulaplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = 2) +
  labs(title = "Distribution of MPG", x = "Miles per gallon", y = "Count")
```

## 12. Histogram — overlapping by group

```{r}
tulaplot(mtcars, aes(x = mpg, fill = factor(cyl))) +
  geom_histogram(binwidth = 2, alpha = 0.6, position = "identity") +
  scale_fill_tula() +
  labs(title = "MPG distribution by cylinder count",
       x = "Miles per gallon", y = "Count", fill = "Cylinders")
```

## 13. Boxplot — single (stc1 blue fill)

```{r}
tulaplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_boxplot() +
  labs(title = "MPG by cylinders", x = "Cylinders", y = "Miles per gallon")
```

## 14. Boxplot — colored by group

```{r}
tulaplot(mtcars, aes(x = factor(cyl), y = mpg, fill = factor(cyl))) +
  geom_boxplot() +
  scale_fill_tula() +
  theme(legend.position = "none") +
  labs(title = "MPG by cylinders (colored)", x = "Cylinders",
       y = "Miles per gallon")
```

## 15. Density plot — overlapping groups

```{r}
tulaplot(mtcars, aes(x = mpg, fill = factor(cyl))) +
  geom_density(alpha = 0.5) +
  scale_fill_tula() +
  labs(title = "MPG density by cylinders", x = "Miles per gallon",
       y = "Density", fill = "Cylinders")
```

## 16. Bar chart — simple counts (stc1 blue fill)

```{r}
tulaplot(mtcars, aes(x = factor(gear))) +
  geom_bar() +
  labs(title = "Number of cars by gear count", x = "Gears", y = "Count")
```

## 17. Stacked bar chart

```{r}
tulaplot(mtcars, aes(x = factor(cyl), fill = factor(gear))) +
  geom_bar() +
  scale_fill_tula() +
  labs(title = "Cylinders with gear breakdown (stacked)",
       x = "Cylinders", y = "Count", fill = "Gears")
```

## 18. Scatter with smooth line

```{r}
tulaplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Weight vs MPG with linear fit",
       x = "Weight (1000 lbs)", y = "Miles per gallon")
```

## 19. Scatter with smooth — grouped

```{r}
tulaplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_tula() +
  labs(title = "Grouped linear fits",
       x = "Weight (1000 lbs)", y = "Miles per gallon",
       color = "Cylinders")
```

## 20. Violin plot

```{r}
tulaplot(mtcars, aes(x = factor(cyl), y = mpg, fill = factor(cyl))) +
  geom_violin(trim = FALSE) +
  scale_fill_tula() +
  theme(legend.position = "none") +
  labs(title = "MPG violin plots by cylinders",
       x = "Cylinders", y = "Miles per gallon")
```

## 21. Jitter/strip plot

```{r}
tulaplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_jitter(width = 0.2, size = 2) +
  labs(title = "Jittered points by cylinders",
       x = "Cylinders", y = "Miles per gallon")
```

## 22. Facet grid — two variables

```{r}
tulaplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  facet_grid(am ~ cyl, labeller = labeller(
    am = c("0" = "Automatic", "1" = "Manual"))) +
  labs(title = "Facet grid: transmission x cylinders")
```

## Using `theme_tula()` standalone with plain `ggplot()`

These tests show that `theme_tula()` can be added to any ggplot — including
plots built by other packages — to get the tula look.

## 23. `ggplot()` + `theme_tula()` — scatterplot

```{r}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  theme_tula() +
  labs(title = "Plain ggplot() + theme_tula()")
```

## 24. `ggplot()` + `theme_tula()` — bar chart with thin black outlines

```{r}
ggplot(mtcars, aes(x = factor(cyl))) +
  geom_bar() +
  theme_tula() +
  labs(title = "Plain ggplot() bar chart + theme_tula()",
       x = "Cylinders", y = "Count")
```

## 25. `ggplot()` + `theme_tula()` — line plot

```{r}
ggplot(economics, aes(x = date, y = unemploy / 1000)) +
  geom_line() +
  theme_tula() +
  labs(title = "Plain ggplot() line plot + theme_tula()",
       x = "Date", y = "Unemployed (millions)")
```

## 26. `ggplot()` + `theme_tula()` — grouped with tula color scale

```{r}
ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  scale_color_tula() +
  theme_tula() +
  labs(title = "ggplot() + scale_color_tula() + theme_tula()",
       x = "Weight (1000 lbs)", y = "Miles per gallon",
       color = "Cylinders")
```

## 27. `ggplot()` + `theme_tula()` — histogram

```{r}
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = 2) +
  theme_tula() +
  labs(title = "Plain ggplot() histogram + theme_tula()",
       x = "Miles per gallon", y = "Count")
```

## 28. `ggplot()` + `theme_tula()` — faceted boxplot

```{r}
ggplot(mtcars, aes(x = factor(vs), y = mpg, fill = factor(vs))) +
  geom_boxplot() +
  scale_fill_tula() +
  facet_wrap(~ cyl) +
  theme_tula() +
  theme(legend.position = "none") +
  labs(title = "ggplot() faceted boxplot + theme_tula()",
       x = "Engine type", y = "Miles per gallon")
```

## 29. All 15 palette colors displayed

```{r}
df15 <- data.frame(
  x = 1:15, y = rep(1, 15),
  color = factor(1:15, levels = 1:15)
)
tulaplot(df15, aes(x = color, y = y, fill = color)) +
  geom_col(width = 0.8) +
  scale_fill_tula() +
  theme(legend.position = "none") +
  labs(title = "All 15 Stata 18 stcolor palette colors",
       x = "stc1 through stc15", y = "")
```
