---
title: "tula — Visual Test Script"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
devtools::load_all(".")
```

# Linear models (lm)

## Test 1 — Simple lm, all numeric predictors

**Expected:** Two-column header with AIC/BIC on left, N/R²/Adj R² on right.
Coefficient table with `cyl`, `wt`, `hp`. Intercept at bottom after separator.
Default output includes 95% CI columns (wide mode auto-activates at width ≥ 80).

```{r}
m1 <- lm(mpg ~ cyl + wt + hp, data = mtcars)
tula(m1)
```

```{r}
cat("Explicitly narrow (wide = FALSE):\n")
tula(m1, wide = FALSE)
```

## Test 2 — lm with a pre-created factor variable

**Expected:** `cyl_f` appears as a group header row; levels `6` and `8` are
indented below it. Reference level (`4`) does not appear. Default is wide.

```{r}
mtcars$cyl_f <- factor(mtcars$cyl)
m2 <- lm(mpg ~ cyl_f + wt, data = mtcars)
tula(m2)
```

## Test 3 — lm with `factor()` inline in formula

**Expected:** Same grouping behavior as Test 2. The group header labels read
`cyl` and `am` (the `factor()` wrapper is stripped for display).

```{r}
m3 <- lm(mpg ~ factor(cyl) + factor(am) + wt, data = mtcars)
tula(m3)
```

## Test 4 — lm with a three-level factor (iris Species)

**Expected:** `Species` header row; levels `versicolor` and `virginica`
indented below it. `setosa` (the reference) does not appear.

```{r}
m4 <- lm(Sepal.Length ~ Sepal.Width + Species, data = iris)
tula(m4)
```

## Test 5 — lm with an interaction term

**Expected:** The interaction `cyl:factor(am)1` is NOT grouped under a factor
header — it prints as a plain row. The `factor(am)` levels are grouped normally.

```{r}
m5 <- lm(mpg ~ cyl * factor(am) + wt, data = mtcars)
tula(m5)
```

---

# Generalized linear models (glm)

## Test 6 — Logistic regression (binomial)

**Expected:** Family/link line at top. Header left: AIC, BIC, Log likelihood.
Header right: N, McFadden R-sq, Nagelkerke R-sq. Coefficient table uses `z`
and `P>|z|`.

```{r}
m6 <- glm(am ~ cyl + wt, data = mtcars, family = binomial)
tula(m6)
```

## Test 7 — Logistic regression with factor predictor

**Expected:** Factor grouping in glm output: `cyl` header row with indented
non-reference levels.

```{r}
m7 <- glm(am ~ factor(cyl) + wt, data = mtcars, family = binomial)
tula(m7)
```

## Test 8 — Poisson regression

**Expected:** `Family: poisson / Link: log` at top. Stat column header is `z`.

```{r}
mtcars$cyl_c <- mtcars$cyl - mean(mtcars$cyl)
m8 <- glm(carb ~ cyl_c + wt, data = mtcars, family = poisson)
tula(m8)
```

## Test 9 — Gaussian glm (should show `t`, not `z`)

**Expected:** `Family: gaussian / Link: identity`. Stat column should be `t`
and p-value header should be `P>|t|`.

```{r}
m9 <- glm(mpg ~ cyl + wt, data = mtcars, family = gaussian)
tula(m9)
```

## Test 10 — Probit link

**Expected:** `Family: binomial / Link: probit`. Otherwise same structure as
logistic output.

```{r}
m10 <- glm(am ~ cyl + wt, data = mtcars, family = binomial(link = "probit"))
tula(m10)
```

---

# Ordered regression (polr / clm)

```{r}
library(MASS)
mtcars$gear_ord <- factor(mtcars$gear, ordered = TRUE)
```

## Test 11 — polr: basic numeric predictors

**Expected:** `Ordered regression / Link: logistic` family label above header.
Header left: AIC, BIC, Log likelihood. Header right: N, McFadden R-sq.
Predictor rows use `z` / `P>|z|`. Cutpoints (`3|4`, `4|5`) appear after an
extra separator, with Coef. and Std. Err. populated but `z` and `P>|z|` blank.

```{r}
m11 <- polr(gear_ord ~ mpg + wt, data = mtcars, Hess = TRUE)
tula(m11)
```

## Test 12 — polr: factor predictor + cutpoints

**Expected:** Stata-style factor group header (`cyl`) with indented levels
in the predictor section, *and* cutpoints in the lower section.

```{r}
m12 <- polr(gear_ord ~ mpg + factor(cyl), data = mtcars, Hess = TRUE)
tula(m12)
```

```{r}
cat("ref = TRUE:\n")
tula(m12, ref = TRUE)
```

## Test 13 — polr: exp = TRUE (odds ratios, cutpoints unaffected)

**Expected:** Predictor rows show `exp(b)` / `DMSE`. Cutpoint rows are **not**
exponentiated (cutpoints are threshold parameters, not log-odds).

```{r}
tula(m12, exp = TRUE)
```

## Test 14 — polr: four-level outcome (three cutpoints)

**Expected:** Three cutpoint rows (`XS|S`, `S|M`, `M|L`).

```{r}
iris4 <- iris
iris4$size <- cut(iris$Sepal.Length,
                  breaks = quantile(iris$Sepal.Length, c(0, .25, .5, .75, 1)),
                  labels = c("XS", "S", "M", "L"),
                  include.lowest = TRUE,
                  ordered_result = TRUE)
m14 <- polr(size ~ Sepal.Width + Petal.Length + Species, data = iris4, Hess = TRUE)
tula(m14)
```

## Test 15 — polr: probit link

**Expected:** Family label reads `Ordered regression / Link: probit`.

```{r}
m15 <- polr(gear_ord ~ mpg + wt, data = mtcars, method = "probit", Hess = TRUE)
tula(m15)
```

## Test 16 — clm (ordinal package)

**Expected:** Output structurally identical to the matching polr model (Test 12).
Family label reads `Ordered regression / Link: logit`. Coefficients should
agree closely (minor differences from optimiser tolerance).

```{r}
if (requireNamespace("ordinal", quietly = TRUE)) {
  library(ordinal)
  mc16 <- clm(gear_ord ~ mpg + factor(cyl), data = mtcars)
  cat("clm (ordinal):\n")
  tula(mc16)
  cat("\npolr (MASS) — same model for comparison:\n")
  tula(m12)
} else {
  cat("ordinal package not installed — clm test skipped.\n")
}
```

## Test 17 — Lowest/Highest footer: short numeric level names

**Expected:** Footer reads `Lowest level: 3, Highest: 5` (the three gear
levels). Appears on the line immediately after the closing separator.

```{r}
tula(m11)
```

## Test 18 — Lowest/Highest footer: string level names (four levels)

**Expected:** Footer reads `Lowest level: XS, Highest: L`, correctly
identifying the first and last levels of the ordered factor.

```{r}
tula(m14)
```

## Test 19 — Lowest/Highest footer: truncation at narrow width

**Expected:** Footer level names are truncated with `~` when the output is
narrow. Each name gets half the available space.

```{r}
iris4b <- iris
iris4b$verbosity <- factor(
  cut(iris$Sepal.Length,
      breaks = quantile(iris$Sepal.Length, c(0, 1/3, 2/3, 1)),
      labels = c("Quite short sepal length",
                 "Medium length sepal",
                 "Very long sepal indeed"),
      include.lowest = TRUE,
      ordered_result = TRUE)
)
m19b <- polr(verbosity ~ Sepal.Width + Petal.Length, data = iris4b, Hess = TRUE)
cat("Wide (labels fit):\n")
tula(m19b)
cat("\nNarrow width = 60 (labels truncated):\n")
tula(m19b, width = 60)
```

## Test 20 — Lowest/Highest footer: clm with string levels

**Expected:** Footer uses the actual outcome level labels, same as the
equivalent polr output (Test 17).

```{r}
if (requireNamespace("ordinal", quietly = TRUE)) {
  cat("clm:\n")
  tula(mc16)
} else {
  cat("ordinal package not installed — skipped.\n")
}
```

---

# Negative binomial (MASS::glm.nb)

## Test 21 — negbin: basic numeric predictors

**Expected:** Family label `"Family: Negative Binomial / Link: log"`.
Header: AIC, BIC, Log likelihood (left), Number of obs, McFadden R-sq (right).
Coefficient table with `z` / `P>|z|`. Ancillary section at bottom with
`/lnalpha` and `alpha` rows, each preceded by a separator.

```{r}
m21 <- glm.nb(carb ~ wt + hp, data = mtcars)
tula(m21)
```

## Test 22 — negbin: factor predictor

**Expected:** `cyl` appears as a grouped factor header with indented levels
`6` and `8`. Ancillary section unchanged.

```{r}
m22 <- glm.nb(carb ~ wt + factor(cyl), data = mtcars)
tula(m22)
```

```{r}
cat("ref = TRUE:\n")
tula(m22, ref = TRUE)
```

## Test 23 — negbin: exp = TRUE (IRR)

**Expected:** Column header reads `"IRR"` (not `"exp(b)"`). SE column reads
`"DMSE"`. Coefficients are exponentiated. Ancillary section (`/lnalpha` and
`alpha`) is NOT exponentiated.

```{r}
tula(m22, exp = TRUE, ref = TRUE)
```

## Test 24 — negbin: width constraints

**Expected:** Long variable names are truncated with `~`. All rows (including
ancillary) have the same total width.

```{r}
df24 <- mtcars
df24$very_long_variable_name <- mtcars$hp
m24 <- glm.nb(carb ~ wt + very_long_variable_name + factor(cyl), data = df24)
tula(m24, width = 68)
```

## Test 25 — negbin vs Poisson comparison

**Expected:** Coefficient signs and rough magnitudes similar between NB and
Poisson. The NB model has an ancillary section; the Poisson does not.

```{r}
cat("Negative binomial:\n")
tula(m21)
cat("\nPoisson:\n")
m_pois <- glm(carb ~ wt + hp, data = mtcars, family = poisson)
tula(m_pois)
```

---

# Quantile regression (quantreg::rq)

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  library(quantreg)
} else {
  cat("quantreg package not installed — quantile regression tests skipped.\n")
}
```

## Test 26 — rq: median regression (tau = 0.5)

**Expected:** Family label reads `"Median regression"`. Header left: Raw sum
of dev, Min sum of dev, K-B Pseudo R2. Header right: Number of obs. Stat
column is `t` / `P>|t|`. Default output includes 95% CI columns.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  m26 <- rq(mpg ~ cyl + wt + hp, data = mtcars, tau = 0.5)
  tula(m26)
}
```

## Test 27 — rq: 90th quantile

**Expected:** Family label reads `"90th Quantile regression"`.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  m27 <- rq(mpg ~ cyl + wt + hp, data = mtcars, tau = 0.9)
  tula(m27)
}
```

## Test 28 — rq: 25th quantile

**Expected:** Family label reads `"25th Quantile regression"`.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  m28 <- rq(mpg ~ cyl + wt + hp, data = mtcars, tau = 0.25)
  tula(m28)
}
```

## Test 29 — rq: factor predictor

**Expected:** `cyl` appears as a grouped factor header with indented levels.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  m29 <- rq(mpg ~ factor(cyl) + wt, data = mtcars, tau = 0.5)
  tula(m29)
}
```

## Test 30 — rq: exp = TRUE

**Expected:** Column headers change to `exp(b)` and `DMSE`. CIs suppressed.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  tula(m27, exp = TRUE)
}
```

## Test 31 — rq: narrow output (wide = FALSE)

**Expected:** No CI columns.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  tula(m26, wide = FALSE)
}
```

## Test 32 — rqs: multiple quantiles (stacked layout)

**Expected:** Shared header with N. One coefficient table per quantile, each
with its own label (e.g. `"25th Quantile regression"`, `"Median regression"`,
`"75th Quantile regression"`). Separated by dashed lines.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  m32 <- rq(mpg ~ cyl + wt + hp, data = mtcars, tau = c(0.25, 0.5, 0.75))
  tula(m32)
}
```

## Test 33 — rqs: multiple quantiles (parallel layout)

**Expected:** Side-by-side columns for each quantile. Coefficient on first
line with significance stars, SE in parentheses on second line.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  tula(m32, parallel = TRUE)
}
```

## Test 34 — rqs: five quantiles stacked

**Expected:** Five blocks: 10th, 25th, 50th, 75th, 90th.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  m34 <- rq(mpg ~ cyl + wt, data = mtcars,
            tau = c(0.10, 0.25, 0.50, 0.75, 0.90))
  tula(m34)
}
```

## Test 35 — rqs: five quantiles parallel

**Expected:** Five side-by-side columns. May require wide output.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  tula(m34, parallel = TRUE, width = 120)
}
```

## Test 36 — rq: ref = TRUE with factor

**Expected:** Reference-level row appears with `0` in Coef. column.

```{r}
if (requireNamespace("quantreg", quietly = TRUE)) {
  tula(m29, ref = TRUE)
}
```

---

# ref = TRUE — Reference level rows

## Test 37 — Single factor, lm

**Expected:** `ref = FALSE` (default) shows only non-reference levels (`6`, `8`).
`ref = TRUE` adds a `4 (base)` row at the bottom of the `cyl` group with
`0` in the Coef. column and blanks for SE, t, and P>|t|.

```{r}
m37 <- lm(mpg ~ factor(cyl) + wt, data = mtcars)
cat("ref = FALSE (default):\n")
tula(m37)
cat("\nref = TRUE:\n")
tula(m37, ref = TRUE)
```

## Test 38 — Two factors, lm

**Expected:** Each factor group gets its own `(base)` row. `cyl` base = `4`;
`am` base = `0`.

```{r}
m38 <- lm(mpg ~ factor(cyl) + factor(am) + wt, data = mtcars)
tula(m38, ref = TRUE)
```

## Test 39 — glm with factor predictor

**Expected:** Reference row appears in the glm coefficient table just as in lm.
Stat column is `z`; p-value column is `P>|z|`.

```{r}
m39 <- glm(am ~ factor(cyl) + wt, data = mtcars, family = binomial)
tula(m39, ref = TRUE)
```

## Test 40 — Three-level factor (iris)

**Expected:** `setosa` appears as the base row after `versicolor` and
`virginica`.

```{r}
m40 <- lm(Sepal.Length ~ Sepal.Width + Species, data = iris)
cat("ref = FALSE (default):\n")
tula(m40)
cat("\nref = TRUE:\n")
tula(m40, ref = TRUE)
```

## Test 41 — Long factor labels (truncation check)

**Expected:** Factor level labels long enough to require truncation (`~`).
The base-category row should truncate cleanly, and all rows must be the same
width as the separator lines.

```{r}
df41 <- mtcars
df41$engine_type <- factor(
  mtcars$cyl,
  levels = c(4, 6, 8),
  labels = c("Four-cylinder inline engine",
             "Six-cylinder inline engine",
             "Eight-cylinder V-type engine")
)
m41 <- lm(mpg ~ wt + engine_type, data = df41)
tula(m41, ref = TRUE)
```

## Test 42 — Binary factor collapse

**Expected:** When a binary factor's non-reference level label matches the
variable name (case-insensitively), the group-header row is suppressed and the
coefficient prints directly on the variable name row (no indentation).
`male` should appear once, not as a header + indented row. `treatment` does
NOT collapse because the non-ref level is `treated` ≠ `treatment`.

```{r}
df42 <- mtcars
df42$male <- factor(ifelse(mtcars$am == 1, "male", "female"),
                    levels = c("female", "male"))
df42$treatment <- factor(ifelse(mtcars$am == 1, "treated", "control"),
                         levels = c("control", "treated"))
m42 <- lm(mpg ~ wt + male + treatment, data = df42)
cat("Default (ref = FALSE) — 'male' collapses, 'treatment' does not:\n")
tula(m42)
cat("\nref = TRUE — collapse suppressed (male has 2 rows):\n")
tula(m42, ref = TRUE)
```

---

# label — Haven-style value labels

## Test 43 — Factor levels already meaningful strings

**Expected:** `label = TRUE` and `label = FALSE` produce identical output when
levels are already strings (e.g. `"Four"`, `"Six"`, `"Eight"`).

```{r}
df43 <- mtcars
df43$cyl_named <- factor(mtcars$cyl,
                         levels = c(4, 6, 8),
                         labels = c("Four", "Six", "Eight"))
m43 <- lm(mpg ~ cyl_named + wt, data = df43)
cat("label = TRUE (default):\n")
tula(m43, ref = TRUE, label = TRUE)
cat("\nlabel = FALSE:\n")
tula(m43, ref = TRUE, label = FALSE)
```

## Test 44 — Haven-style value labels

**Expected:** When the data column carries a `labels` attribute (as produced
by haven), `label = TRUE` substitutes numeric codes with text labels.
`label = FALSE` shows raw numeric suffixes.

```{r}
df44 <- mtcars
df44$cyl_lbl <- mtcars$cyl
attr(df44$cyl_lbl, "labels") <- c("Four cylinders" = 4,
                                   "Six cylinders"  = 6,
                                   "Eight cylinders" = 8)
m44 <- lm(mpg ~ factor(cyl_lbl) + wt, data = df44)
cat("label = TRUE (default) — shows full label text:\n")
tula(m44, ref = TRUE, label = TRUE)
cat("\nlabel = FALSE — shows raw numeric suffixes:\n")
tula(m44, ref = TRUE, label = FALSE)
```

---

# exp = TRUE — Exponentiated coefficients

## Test 45 — lm, numeric predictors

**Expected:** Column headers change to `exp(b)` and `DMSE`. Estimate column
shows `exp(coef)`, SE column shows `exp(coef) * SE`. `t` and `P>|t|`
unchanged. CIs suppressed.

```{r}
m45 <- lm(mpg ~ cyl + wt, data = mtcars)
cat("exp = FALSE (default):\n")
tula(m45, wide = FALSE)
cat("\nexp = TRUE:\n")
tula(m45, exp = TRUE)
```

## Test 46 — lm with factor and ref = TRUE

**Expected:** Factor header row blank. Non-reference levels show exponentiated
coefficients and DMSE. Reference-level row shows `1` instead of `0`.

```{r}
m46 <- lm(mpg ~ factor(cyl) + wt, data = mtcars)
tula(m46, exp = TRUE, ref = TRUE)
```

## Test 47 — glm logistic (odds ratios)

**Expected:** `exp(b)` produces odds ratios for logistic model. Compare with
R's `exp(coef(m))`.

```{r}
m47 <- glm(am ~ cyl + wt, data = mtcars, family = binomial)
cat("exp = TRUE (odds ratios):\n")
tula(m47, exp = TRUE)
cat("\nVerification — exp(coef):\n")
print(exp(coef(m47)))
```

## Test 48 — glm with factor and ref = TRUE

**Expected:** Reference rows show `1`. Factor headers blank. Stat and p-value
unchanged.

```{r}
m48 <- glm(am ~ factor(cyl) + wt, data = mtcars, family = binomial)
tula(m48, exp = TRUE, ref = TRUE)
```

---

# level — Confidence interval width

## Test 49 — 90% vs 95% vs 99% CIs

**Expected:** CI bounds narrow at 90% and widen at 99%. Column header updates:
`[90% Conf`, `[95% Conf`, `[99% Conf`. Point estimates, SEs, statistics, and
p-values are identical across all three.

```{r}
m49 <- lm(mpg ~ cyl + wt, data = mtcars)
cat("level = 90:\n")
tula(m49, level = 90)
cat("\nlevel = 95 (default):\n")
tula(m49)
cat("\nlevel = 99:\n")
tula(m49, level = 99)
```

## Test 50 — Proportion input and error handling

**Expected:** `level = 0.90` is treated the same as `level = 90` (auto-multiplied
by 100). `level = 40` produces an error.

```{r}
cat("level = 0.90 (same as 90):\n")
tula(m49, level = 0.90)
cat("\nlevel = 40 (should error):\n")
tryCatch(
  tula(m49, level = 40),
  error = function(e) cat("Error caught:", conditionMessage(e), "\n")
)
```

---

# wide / width — Display options

## Test 51 — exp = TRUE suppresses CIs with a message

**Expected:** A message is printed ("Note: wide output is not yet supported
with exp = TRUE; CIs suppressed.") and the output has no CI columns.

```{r}
m51 <- lm(mpg ~ cyl + wt, data = mtcars)
cat("exp = TRUE, wide = TRUE (should message, suppress CIs):\n")
tula(m51, exp = TRUE, wide = TRUE)
```

## Test 52 — exp = TRUE with explicit wide = FALSE (no message)

**Expected:** No message about CIs when `wide = FALSE` is set explicitly.

```{r}
cat("exp = TRUE, wide = FALSE (should NOT message):\n")
tula(m51, exp = TRUE, wide = FALSE)
```

## Test 53 — width below minimum (warning + clamp to 60)

**Expected:** A warning is issued ("width cannot be less than 60; using
width = 60.") and the output is produced at width = 60.

```{r}
cat("width = 40 (should warn and use 60):\n")
withCallingHandlers(
  tula(lm(mpg ~ wt + cyl, data = mtcars), width = 40),
  warning = function(w) { cat("Warning:", conditionMessage(w), "\n"); invokeRestart("muffleWarning") }
)
```

---

# Edge cases

## Test 54 — Very small p-values

**Expected:** p-values below 0.0001 display as `<.0001`.

```{r}
m54 <- lm(Sepal.Length ~ Petal.Length + Petal.Width + Species, data = iris)
tula(m54)
```

## Test 55 — Single predictor (minimal model)

**Expected:** Header and table format correctly with just one covariate row
plus the intercept.

```{r}
m55 <- lm(mpg ~ wt, data = mtcars)
tula(m55)
```

## Test 56 — Ordered factor as predictor

**Expected:** Ordered factors are treated the same as regular factors — grouped
under a header row with indented levels.

```{r}
mtcars$gear_o <- factor(mtcars$gear, ordered = TRUE)
m56 <- lm(mpg ~ gear_o + wt, data = mtcars)
tula(m56)
```

## Test 57 — glm with small sample (stress test)

```{r}
iris_bin <- iris
iris_bin$is_virginica <- as.integer(iris_bin$Species == "virginica")
m57 <- glm(is_virginica ~ Sepal.Length + Sepal.Width,
           data = iris_bin, family = binomial)
tula(m57)
```

## Test 58 — Unsupported object type (error handling)

**Expected:** A clear, informative error message naming the unsupported class.

```{r}
tryCatch(
  tula(list(x = 1, y = 2)),
  error = function(e) cat("Error caught as expected:\n", conditionMessage(e), "\n")
)
```
