---
title: "tula — Visual Test Script"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
# Load the tula package from source.
# Run this script from the Koala/ package directory, or set the path below.
devtools::load_all(".")
```

---

## Test 1 — Simple lm, all numeric predictors

**Expected:** Two-column header with AIC/BIC on left, N/R²/Adj R² on right.
Coefficient table with `cyl`, `wt`, `hp`. Intercept at bottom after separator.
No CI columns in narrow mode; CI columns appear in wide mode.

```{r test1-narrow}
m1 <- lm(mpg ~ cyl + wt + hp, data = mtcars)
cat("Narrow (default):\n")
tula(m1)
```

```{r test1-wide}
cat("Wide (with 95% CI):\n")
tula(m1, wide = TRUE)
```

---

## Test 2 — lm with a pre-created factor variable

**Expected:** `cyl_f` appears as a group header row; levels `6` and `8` are
indented below it. Reference level (`4`) does not appear.

```{r test2}
mtcars$cyl_f <- factor(mtcars$cyl)
m2 <- lm(mpg ~ cyl_f + wt, data = mtcars)
cat("Narrow:\n")
tula(m2)
cat("\nWide:\n")
tula(m2, wide = TRUE)
```

---

## Test 3 — lm with `factor()` inline in formula

**Expected:** Same grouping behavior as Test 2. The group header labels read
`cyl` and `am` (the `factor()` wrapper is stripped for display).

```{r test3}
m3 <- lm(mpg ~ factor(cyl) + factor(am) + wt, data = mtcars)
cat("Narrow:\n")
tula(m3)
cat("\nWide:\n")
tula(m3, wide = TRUE)
```

---

## Test 4 — lm with a three-level factor (iris Species)

**Expected:** `Species` header row; levels `versicolor` and `virginica`
indented below it. `setosa` (the reference) does not appear.

```{r test4}
m4 <- lm(Sepal.Length ~ Sepal.Width + Species, data = iris)
cat("Narrow:\n")
tula(m4)
cat("\nWide:\n")
tula(m4, wide = TRUE)
```

---

## Test 5 — lm with an interaction term

**Expected:** The interaction `cyl:factor(am)1` is NOT grouped under a factor
header — it prints as a plain row. The `factor(am)` levels are grouped normally.

```{r test5}
m5 <- lm(mpg ~ cyl * factor(am) + wt, data = mtcars)
cat("Narrow:\n")
tula(m5)
```

---

## Test 6 — glm binomial (logistic regression)

**Expected:** Family/link line at top. Header left: AIC, BIC, Log likelihood.
Header right: N, McFadden R-sq, Nagelkerke R-sq. Coefficient table uses `z`
and `P>|z|`.

```{r test6}
m6 <- glm(am ~ cyl + wt, data = mtcars, family = binomial)
cat("Narrow:\n")
tula(m6)
cat("\nWide:\n")
tula(m6, wide = TRUE)
```

---

## Test 7 — glm binomial with factor predictor

**Expected:** Factor grouping in glm output: `factor(cyl)` header row with
indented non-reference levels.

```{r test7}
m7 <- glm(am ~ factor(cyl) + wt, data = mtcars, family = binomial)
cat("Narrow:\n")
tula(m7)
cat("\nWide:\n")
tula(m7, wide = TRUE)
```

---

## Test 8 — glm Poisson

**Expected:** `Family: poisson / Link: log` at top. Stat column header is `z`.

```{r test8}
# Center cyl to avoid perfect separation
mtcars$cyl_c <- mtcars$cyl - mean(mtcars$cyl)
m8 <- glm(carb ~ cyl_c + wt, data = mtcars, family = poisson)
cat("Narrow:\n")
tula(m8)
cat("\nWide:\n")
tula(m8, wide = TRUE)
```

---

## Test 9 — glm Gaussian (should show `t`, not `z`)

**Expected:** `Family: gaussian / Link: identity`. Stat column should be `t`
and p-value header should be `P>|t|`.

```{r test9}
m9 <- glm(mpg ~ cyl + wt, data = mtcars, family = gaussian)
tula(m9)
```

---

## Test 10 — Very small p-values (edge case)

**Expected:** p-values below 0.0001 display as `< .0001`.

```{r test10}
m10 <- lm(Sepal.Length ~ Petal.Length + Petal.Width + Species, data = iris)
tula(m10)
```

---

## Test 11 — Single predictor (minimal model)

**Expected:** Header and table format correctly with just one covariate row
plus the intercept.

```{r test11}
m11 <- lm(mpg ~ wt, data = mtcars)
cat("Narrow:\n")
tula(m11)
cat("\nWide:\n")
tula(m11, wide = TRUE)
```

---

## Test 12 — Ordered factor

**Expected:** Ordered factors are treated the same as regular factors — grouped
under a header row with indented levels.

```{r test12}
mtcars$gear_o <- factor(mtcars$gear, ordered = TRUE)
m12 <- lm(mpg ~ gear_o + wt, data = mtcars)
tula(m12)
```

---

## Test 13 — glm with factor and small sample (stress test)

```{r test13}
# Use only a subset of iris for a binomial model
iris_bin <- iris
iris_bin$is_virginica <- as.integer(iris_bin$Species == "virginica")
m13 <- glm(is_virginica ~ Sepal.Length + Sepal.Width,
           data = iris_bin, family = binomial)
cat("Narrow:\n")
tula(m13)
cat("\nWide:\n")
tula(m13, wide = TRUE)
```

---

## Test 14 — Error handling: unsupported object type

**Expected:** A clear, informative error message naming the unsupported class.

```{r test14}
tryCatch(
  tula(list(x = 1, y = 2)),
  error = function(e) cat("Error caught as expected:\n", conditionMessage(e), "\n")
)
```

---

## Test 15 — glm with probit link

**Expected:** `Family: binomial / Link: probit`. Otherwise same structure as
logistic output.

```{r test15}
m15 <- glm(am ~ cyl + wt, data = mtcars, family = binomial(link = "probit"))
tula(m15)
```

---

## Test 16 — `ref = TRUE`: single factor, lm

**Expected:** `ref = FALSE` (default) shows only non-reference levels (`6`, `8`).
`ref = TRUE` appends a `4 (base)` row at the bottom of the `cyl` group with
`0` in the Coef. column and blanks for SE, t, and P>|t|.

```{r test16}
m16 <- lm(mpg ~ factor(cyl) + wt, data = mtcars)
cat("ref = FALSE (default):\n")
tula(m16)
cat("\nref = TRUE:\n")
tula(m16, ref = TRUE)
cat("\nref = TRUE, wide = TRUE:\n")
tula(m16, ref = TRUE, wide = TRUE)
```

---

## Test 17 — `ref = TRUE`: two factors, lm

**Expected:** Each factor group gets its own `(base)` row appended after its
non-reference levels. `cyl` base = `4`; `am` base = `0`.

```{r test17}
m17 <- lm(mpg ~ factor(cyl) + factor(am) + wt, data = mtcars)
cat("ref = TRUE, narrow:\n")
tula(m17, ref = TRUE)
cat("\nref = TRUE, wide:\n")
tula(m17, ref = TRUE, wide = TRUE)
```

---

## Test 18 — `ref = TRUE`: glm with factor predictor

**Expected:** Reference row appears in the glm coefficient table just as in lm.
Stat column is `z`; p-value column is `P>|z|`. CI columns blank on ref row
when `wide = TRUE`.

```{r test18}
m18 <- glm(am ~ factor(cyl) + wt, data = mtcars, family = binomial)
cat("ref = TRUE, narrow:\n")
tula(m18, ref = TRUE)
cat("\nref = TRUE, wide:\n")
tula(m18, ref = TRUE, wide = TRUE)
```

---

## Test 19 — `ref = TRUE`: three-level factor (iris)

**Expected:** `setosa` appears as the base row after `versicolor` and
`virginica`. All other columns blank on that row.

```{r test19}
m19 <- lm(Sepal.Length ~ Sepal.Width + Species, data = iris)
cat("ref = FALSE (default):\n")
tula(m19)
cat("\nref = TRUE:\n")
tula(m19, ref = TRUE)
```

---

## Test 20 — `label = TRUE` with factor levels that already are label strings

**Expected:** When a factor variable's levels are already meaningful strings
(e.g. `"Four"`, `"Six"`, `"Eight"`), `label = TRUE` and `label = FALSE` produce
identical output — the level names are used as-is.

```{r test20}
df20 <- mtcars
df20$cyl_named <- factor(mtcars$cyl,
                          levels = c(4, 6, 8),
                          labels = c("Four", "Six", "Eight"))
m20 <- lm(mpg ~ cyl_named + wt, data = df20)
cat("label = TRUE (default):\n")
tula(m20, ref = TRUE, label = TRUE)
cat("\nlabel = FALSE:\n")
tula(m20, ref = TRUE, label = FALSE)
```

---

## Test 21 — `label = TRUE` with haven-style value labels

**Expected:** When the data column carries a `labels` attribute (as produced
by `haven` when reading SPSS/Stata files), `label = TRUE` substitutes the
numeric codes with their text labels in the output. `label = FALSE` shows
the raw numeric suffixes instead. `tula()` recovers the labels from the
original data even when `factor()` is used inline in the formula (which would
normally strip the attribute).

```{r test21}
df21 <- mtcars
# Simulate a haven_labelled column: a plain numeric with a 'labels' attr.
# In real usage this comes from haven::read_spss() / haven::read_dta().
df21$cyl_lbl <- mtcars$cyl
attr(df21$cyl_lbl, "labels") <- c("Four cylinders" = 4,
                                   "Six cylinders"  = 6,
                                   "Eight cylinders" = 8)

# Wrap in factor() in the formula to get factor grouping in the output.
m21 <- lm(mpg ~ factor(cyl_lbl) + wt, data = df21)
cat("label = TRUE (default) — shows full label text:\n")
tula(m21, ref = TRUE, label = TRUE)
cat("\nlabel = FALSE — shows raw numeric suffixes '4', '6', '8':\n")
tula(m21, ref = TRUE, label = FALSE)
```

---

## Test 22 — `ref = TRUE` alignment check (wide mode, long label)

**Expected:** All rows — including the `(base)` row and factor header rows —
are exactly the same width as the separator lines in wide mode.

```{r test22}
m22 <- lm(Sepal.Length ~ Petal.Length + Petal.Width + Species, data = iris)
tula(m22, ref = TRUE, wide = TRUE)
```
