---
title: "tula — Visual Test Script"
format:
  html:
    embed-resources: true
    code-fold: false
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
# Load the tula package from source.
# Run this script from the package directory, or set the path below.
library(nnet)
devtools::load_all(".")
```

---

# lm basics

## Test 1 — Simple lm, all numeric predictors

**Expected:** Two-column header with AIC/BIC on left, N/R²/Adj R² on right.
Coefficient table with `cyl`, `wt`, `hp`. Intercept at bottom after separator.
No CI columns in narrow mode; CI columns appear in wide mode.

```{r test1-narrow}
m1 <- lm(mpg ~ cyl + wt + hp, data = mtcars)
cat("Narrow (default):\n")
tula(m1)
```

```{r test1-wide}
cat("Wide (with 95% CI):\n")
tula(m1, wide = TRUE)
```

---

## Test 2 — lm with a pre-created factor variable

**Expected:** `cyl_f` appears as a group header row; levels `6` and `8` are
indented below it. Reference level (`4`) does not appear.

```{r test2}
mtcars$cyl_f <- factor(mtcars$cyl)
m2 <- lm(mpg ~ cyl_f + wt, data = mtcars)
cat("Narrow:\n")
tula(m2)
cat("\nWide:\n")
tula(m2, wide = TRUE)
```

---

## Test 3 — lm with `factor()` inline in formula

**Expected:** Same grouping behavior as Test 2. The group header labels read
`cyl` and `am` (the `factor()` wrapper is stripped for display).

```{r test3}
m3 <- lm(mpg ~ factor(cyl) + factor(am) + wt, data = mtcars)
cat("Narrow:\n")
tula(m3)
cat("\nWide:\n")
tula(m3, wide = TRUE)
```

---

## Test 4 — lm with a three-level factor (iris Species)

**Expected:** `Species` header row; levels `versicolor` and `virginica`
indented below it. `setosa` (the reference) does not appear.

```{r test4}
m4 <- lm(Sepal.Length ~ Sepal.Width + Species, data = iris)
cat("Narrow:\n")
tula(m4)
cat("\nWide:\n")
tula(m4, wide = TRUE)
```

---

## Test 5 — lm with an interaction term

**Expected:** The interaction `cyl:factor(am)1` is NOT grouped under a factor
header — it prints as a plain row. The `factor(am)` levels are grouped normally.

```{r test5}
m5 <- lm(mpg ~ cyl * factor(am) + wt, data = mtcars)
cat("Narrow:\n")
tula(m5)
```

---

# glm basics

## Test 6 — glm binomial (logistic regression)

**Expected:** Family/link line at top. Header left: AIC, BIC, Log likelihood.
Header right: N, McFadden R-sq, Nagelkerke R-sq. Coefficient table uses `z`
and `P>|z|`.

```{r test6}
m6 <- glm(am ~ cyl + wt, data = mtcars, family = binomial)
cat("Narrow:\n")
tula(m6)
cat("\nWide:\n")
tula(m6, wide = TRUE)
```

---

## Test 7 — glm binomial with factor predictor

**Expected:** Factor grouping in glm output: `factor(cyl)` header row with
indented non-reference levels.

```{r test7}
m7 <- glm(am ~ factor(cyl) + wt, data = mtcars, family = binomial)
cat("Narrow:\n")
tula(m7)
cat("\nWide:\n")
tula(m7, wide = TRUE)
```

---

## Test 8 — glm Poisson

**Expected:** `Family: poisson / Link: log` at top. Stat column header is `z`.

```{r test8}
# Center cyl to avoid perfect separation
mtcars$cyl_c <- mtcars$cyl - mean(mtcars$cyl)
m8 <- glm(carb ~ cyl_c + wt, data = mtcars, family = poisson)
cat("Narrow:\n")
tula(m8)
cat("\nWide:\n")
tula(m8, wide = TRUE)
```

---

## Test 9 — glm Gaussian (should show `t`, not `z`)

**Expected:** `Family: gaussian / Link: identity`. Stat column should be `t`
and p-value header should be `P>|t|`.

```{r test9}
m9 <- glm(mpg ~ cyl + wt, data = mtcars, family = gaussian)
tula(m9)
```

---

## Test 10 — glm with probit link

**Expected:** `Family: binomial / Link: probit`. Otherwise same structure as
logistic output.

```{r test10}
m10 <- glm(am ~ cyl + wt, data = mtcars, family = binomial(link = "probit"))
tula(m10)
```

---

# multinom basics

## Test 11 — multinom: basic three-outcome model

**Expected:** Shared header (AIC, BIC, Log likelihood / N, McFadden R-sq).
Two outcome blocks (`6`, `8`) each separated by a dashed line with the outcome
label between. `(Intercept)` at the bottom of each block. Footer: `Base outcome: 4`.

```{r test11}
m11 <- multinom(factor(cyl) ~ wt + hp, data = mtcars, trace = FALSE)
cat("Narrow:\n")
tula(m11)
cat("\nWide:\n")
tula(m11, wide = TRUE)
```

---

## Test 12 — multinom: factor predictor, grouping in each block

**Expected:** `am` appears as a grouped factor header with indented level `1`
in every outcome block — the same Stata-style grouping as lm/glm.

```{r test12}
m12 <- multinom(factor(cyl) ~ wt + hp + factor(am), data = mtcars, trace = FALSE)
cat("Narrow:\n")
tula(m12)
```

---

## Test 13 — multinom: four-outcome model

**Expected:** Three outcome blocks (S, M, L with XS as base), each containing
a `Species` factor group and a `Sepal.Width` row. Header and footer correct.

```{r test13}
iris4 <- iris
iris4$size <- cut(iris$Sepal.Length,
                  breaks = quantile(iris$Sepal.Length, c(0, .25, .5, .75, 1)),
                  labels = c("XS", "S", "M", "L"),
                  include.lowest = TRUE)
m13 <- multinom(size ~ Sepal.Width + Species, data = iris4, trace = FALSE)
tula(m13)
```

---

## Test 14 — multinom: long outcome labels (truncation test)

**Expected:** Each outcome label appears on the same line as the column headers
(Coef., Std. Err., z, P>|z|), in the label-column area left of `|`. When an
outcome label is longer than the label column, it is truncated with `~` — the
`|` separator must remain perfectly aligned in every row of the output.
"Base outcome:" remains as a footer below the final separator.

```{r test14}
# Use long, descriptive outcome labels so truncation is exercised.
set.seed(42)
df14 <- data.frame(
  outcome = factor(
    sample(c("Not in labor force", "Part-time employed", "Full-time employed"),
           size = 200, replace = TRUE, prob = c(0.3, 0.3, 0.4)),
    levels = c("Not in labor force", "Part-time employed", "Full-time employed")
  ),
  age    = rnorm(200, mean = 40, sd = 12),
  female = rbinom(200, size = 1, prob = 0.5)
)
m14 <- multinom(outcome ~ age + female, data = df14, trace = FALSE)

cat("Default width:\n")
tula(m14)
cat("\nwide = TRUE:\n")
tula(m14, wide = TRUE)
cat("\nwidth = 68 (forces label truncation):\n")
tula(m14, width = 68)
```

---

## Test 15 — multinom vs glm on binary outcome (sanity check)

**Expected:** Coefficients, SEs, z-stats, and p-values from `multinom()` on a
two-level outcome should match those from `glm(..., family = binomial)` closely
(up to sign conventions — multinom models log-odds of level 2 vs level 1).

```{r test15}
m15_glm <- glm(am ~ wt + hp, data = mtcars, family = binomial)
m15_mn  <- multinom(factor(am) ~ wt + hp, data = mtcars, trace = FALSE)
cat("glm (logistic):\n")
tula(m15_glm)
cat("\nmultinom (binary):\n")
tula(m15_mn)
```

---

# `ref = TRUE`

## Test 16 — `ref = TRUE`: single factor, lm

**Expected:** `ref = FALSE` (default) shows only non-reference levels (`6`, `8`).
`ref = TRUE` appends a `4 (base)` row at the bottom of the `cyl` group with
`0` in the Coef. column and blanks for SE, t, and P>|t|.

```{r test16}
m16 <- lm(mpg ~ factor(cyl) + wt, data = mtcars)
cat("ref = FALSE (default):\n")
tula(m16)
cat("\nref = TRUE:\n")
tula(m16, ref = TRUE)
cat("\nref = TRUE, wide = TRUE:\n")
tula(m16, ref = TRUE, wide = TRUE)
```

---

## Test 17 — `ref = TRUE`: two factors, lm

**Expected:** Each factor group gets its own `(base)` row appended after its
non-reference levels. `cyl` base = `4`; `am` base = `0`.

```{r test17}
m17 <- lm(mpg ~ factor(cyl) + factor(am) + wt, data = mtcars)
cat("ref = TRUE, narrow:\n")
tula(m17, ref = TRUE)
cat("\nref = TRUE, wide:\n")
tula(m17, ref = TRUE, wide = TRUE)
```

---

## Test 18 — `ref = TRUE`: glm with factor predictor

**Expected:** Reference row appears in the glm coefficient table just as in lm.
Stat column is `z`; p-value column is `P>|z|`. CI columns blank on ref row
when `wide = TRUE`.

```{r test18}
m18 <- glm(am ~ factor(cyl) + wt, data = mtcars, family = binomial)
cat("ref = TRUE, narrow:\n")
tula(m18, ref = TRUE)
cat("\nref = TRUE, wide:\n")
tula(m18, ref = TRUE, wide = TRUE)
```

---

## Test 19 — `ref = TRUE`: three-level factor (iris)

**Expected:** `setosa` appears as the base row after `versicolor` and
`virginica`. All other columns blank on that row.

```{r test19}
m19 <- lm(Sepal.Length ~ Sepal.Width + Species, data = iris)
cat("ref = FALSE (default):\n")
tula(m19)
cat("\nref = TRUE:\n")
tula(m19, ref = TRUE)
```

---

## Test 20 — `ref = TRUE`: multinom

**Expected:** Each factor group in every outcome block gets a `0 (base)` row
appended after its non-reference levels. Numeric columns blank on that row.

```{r test20}
m20 <- multinom(factor(cyl) ~ wt + hp + factor(am), data = mtcars, trace = FALSE)
cat("ref = TRUE, narrow:\n")
tula(m20, ref = TRUE)
cat("\nref = TRUE, wide:\n")
tula(m20, ref = TRUE, wide = TRUE)
```

---

## Test 21 — `ref = TRUE` with long factor level labels (truncation check)

**Expected:** Factor level labels long enough to require truncation (`~`) in
the label column. The base-category row (estimate = 0, rest blank) should
truncate cleanly alongside the other rows, and all rows — including the base
row — must be exactly the same width as the separator lines. Run in both
narrow (default) and wide modes.

```{r test21}
df21 <- mtcars
df21$engine_type <- factor(
  mtcars$cyl,
  levels = c(4, 6, 8),
  labels = c("Four-cylinder inline engine",
             "Six-cylinder inline engine",
             "Eight-cylinder V-type engine")
)
m21 <- lm(mpg ~ wt + engine_type, data = df21)
cat("Narrow (ref = TRUE):\n")
tula(m21, ref = TRUE)
cat("\nWide (ref = TRUE):\n")
tula(m21, ref = TRUE, wide = TRUE)
```

---

## Test 21b — binary factor collapse (level name = variable name)

**Expected:** When a binary factor's non-reference level label matches the
variable name (case-insensitively), the group-header row is suppressed and the
coefficient prints directly on the variable name row (no indentation).
`male` should appear once, not as a header + indented row.

Three checks: (1) collapse fires; (2) collapse suppressed when label differs
from name (`treated` ≠ `treatment`); (3) collapse suppressed when `ref = TRUE`
because the ref row makes a second row.

```{r test21b}
df21b <- mtcars
# "male": non-ref level name matches variable name → should collapse
df21b$male <- factor(ifelse(mtcars$am == 1, "male", "female"),
                     levels = c("female", "male"))
# "treatment": non-ref level name does NOT match variable name → no collapse
df21b$treatment <- factor(ifelse(mtcars$am == 1, "treated", "control"),
                          levels = c("control", "treated"))
m21b <- lm(mpg ~ wt + male + treatment, data = df21b)

cat("Default (ref = FALSE) — 'male' collapses, 'treatment' does not:\n")
tula(m21b)
cat("\nref = TRUE — 'male' has 2 rows (no collapse):\n")
tula(m21b, ref = TRUE)
```

---

# `label`

## Test 22 — `label = TRUE` with factor levels that already are label strings

**Expected:** When a factor variable's levels are already meaningful strings
(e.g. `"Four"`, `"Six"`, `"Eight"`), `label = TRUE` and `label = FALSE` produce
identical output — the level names are used as-is.

```{r test22}
df22 <- mtcars
df22$cyl_named <- factor(mtcars$cyl,
                          levels = c(4, 6, 8),
                          labels = c("Four", "Six", "Eight"))
m22 <- lm(mpg ~ cyl_named + wt, data = df22)
cat("label = TRUE (default):\n")
tula(m22, ref = TRUE, label = TRUE)
cat("\nlabel = FALSE:\n")
tula(m22, ref = TRUE, label = FALSE)
```

---

## Test 23 — `label = TRUE` with haven-style value labels

**Expected:** When the data column carries a `labels` attribute (as produced
by `haven` when reading SPSS/Stata files), `label = TRUE` substitutes the
numeric codes with their text labels in the output. `label = FALSE` shows
the raw numeric suffixes instead. `tula()` recovers the labels from the
original data even when `factor()` is used inline in the formula (which would
normally strip the attribute).

```{r test23}
df23 <- mtcars
# Simulate a haven_labelled column: a plain numeric with a 'labels' attr.
# In real usage this comes from haven::read_spss() / haven::read_dta().
df23$cyl_lbl <- mtcars$cyl
attr(df23$cyl_lbl, "labels") <- c("Four cylinders" = 4,
                                   "Six cylinders"  = 6,
                                   "Eight cylinders" = 8)

# Wrap in factor() in the formula to get factor grouping in the output.
m23 <- lm(mpg ~ factor(cyl_lbl) + wt, data = df23)
cat("label = TRUE (default) — shows full label text:\n")
tula(m23, ref = TRUE, label = TRUE)
cat("\nlabel = FALSE — shows raw numeric suffixes '4', '6', '8':\n")
tula(m23, ref = TRUE, label = FALSE)
```

---

# `exp = TRUE`

## Test 24 — `exp = TRUE`: lm, numeric predictors

**Expected:** Column headers change to `exp(b)` and `DMSE`. Estimate column
shows `exp(coef)`, SE column shows `exp(coef) * SE`. The `t` and `P>|t|`
columns are unchanged from the non-exponentiated output. CIs are suppressed.

```{r test24}
m24 <- lm(mpg ~ cyl + wt, data = mtcars)
cat("exp = FALSE (default):\n")
tula(m24)
cat("\nexp = TRUE:\n")
tula(m24, exp = TRUE)
```

---

## Test 25 — `exp = TRUE`: lm with factor and `ref = TRUE`

**Expected:** Factor group header row still blank. Non-reference levels show
exponentiated coefficients and DMSE. Reference-level row shows `1` instead of
`0`. Intercept row is exponentiated normally.

```{r test25}
m25 <- lm(mpg ~ factor(cyl) + wt, data = mtcars)
cat("exp = TRUE, ref = TRUE:\n")
tula(m25, exp = TRUE, ref = TRUE)
cat("\nexp = FALSE, ref = TRUE (comparison):\n")
tula(m25, ref = TRUE)
```

---

## Test 26 — `exp = TRUE`: glm logistic (odds ratios)

**Expected:** For a logistic model, `exp(b)` produces odds ratios. Compare with
R's built-in `exp(coef(m))` to verify values match. DMSE = `exp(b) * SE`.
Stat column is `z`; `P>|z|` unchanged.

```{r test26}
m26 <- glm(am ~ cyl + wt, data = mtcars, family = binomial)
cat("exp = FALSE:\n")
tula(m26)
cat("\nexp = TRUE (odds ratios):\n")
tula(m26, exp = TRUE)
cat("\nVerification — exp(coef):\n")
print(exp(coef(m26)))
```

---

## Test 27 — `exp = TRUE`: glm with factor and `ref = TRUE`

**Expected:** Same as Test 25 but for glm. Reference rows show `1`. Factor
headers blank. Stat and p-value unchanged.

```{r test27}
m27 <- glm(am ~ factor(cyl) + wt, data = mtcars, family = binomial)
cat("exp = TRUE, ref = TRUE:\n")
tula(m27, exp = TRUE, ref = TRUE)
```

---

## Test 28 — `exp = TRUE`: multinom

**Expected:** Each outcome block shows exponentiated coefficients and DMSE.
Column headers `exp(b)` and `DMSE` appear in every block. Footer unchanged.

```{r test28}
m28 <- multinom(factor(cyl) ~ wt + hp, data = mtcars, trace = FALSE)
cat("exp = FALSE:\n")
tula(m28)
cat("\nexp = TRUE:\n")
tula(m28, exp = TRUE)
```

---

## Test 29 — `exp = TRUE`: multinom with factor and `ref = TRUE`

**Expected:** Reference rows in each outcome block show `1`. Factor headers
blank. Exponentiated coefficients and DMSE in all regular rows.

```{r test29}
m29 <- multinom(factor(cyl) ~ wt + hp + factor(am), data = mtcars, trace = FALSE)
cat("exp = TRUE, ref = TRUE:\n")
tula(m29, exp = TRUE, ref = TRUE)
```

---

# `wide` / `width` options

## Test 30 — `exp = TRUE` with `wide = TRUE` (message + suppression)

**Expected:** A message is printed ("Note: wide output is not yet supported
with exp = TRUE; CIs suppressed.") and the output is narrow (no CI columns).
When `exp = FALSE` with `wide = TRUE`, CIs appear normally.

```{r test30}
m30 <- lm(mpg ~ cyl + wt, data = mtcars)
cat("exp = TRUE, wide = TRUE (should message, suppress CIs):\n")
tula(m30, exp = TRUE, wide = TRUE)
cat("\nexp = FALSE, wide = TRUE (CIs should appear):\n")
tula(m30, wide = TRUE)
```

---

## Test 31 — `exp = TRUE` with `wide = FALSE` (no message)

**Expected:** No message about CIs is printed when `wide = FALSE` is set
explicitly, even with `exp = TRUE`.

```{r test31}
m31 <- lm(mpg ~ cyl + wt, data = mtcars)
cat("exp = TRUE, wide = FALSE (should NOT message):\n")
tula(m31, exp = TRUE, wide = FALSE)
```

---

## Test 32 — multinom: `width` option forces label truncation

**Expected:** Long labels truncated with `~` in every outcome block; separators
and all rows the same width.

```{r test32}
df32 <- mtcars
names(df32)[names(df32) == "wt"] <- "vehicle_weight_lbs"
names(df32)[names(df32) == "hp"] <- "gross_horsepower_bhp"
m32 <- multinom(factor(cyl) ~ vehicle_weight_lbs + gross_horsepower_bhp,
                data = df32, trace = FALSE)
cat("Default width:\n")
tula(m32)
cat("\nwidth = 68:\n")
tula(m32, width = 68)
```

---

## Test 33 — `width` below minimum (warning + clamp to 60)

**Expected:** A warning is issued ("width cannot be less than 60; using width = 60.")
and the output is produced at width = 60, not suppressed.

```{r test33}
cat("lm with width = 40 (should warn and use 60):\n")
withCallingHandlers(
  tula(lm(mpg ~ wt + cyl, data = mtcars), width = 40),
  warning = function(w) { cat("Warning:", conditionMessage(w), "\n"); invokeRestart("muffleWarning") }
)

cat("\nmultinom with width = 30 (should warn and use 60):\n")
withCallingHandlers(
  tula(multinom(factor(cyl) ~ wt + hp, data = mtcars, trace = FALSE), width = 30),
  warning = function(w) { cat("Warning:", conditionMessage(w), "\n"); invokeRestart("muffleWarning") }
)
```

---

# Edge cases

## Test 34 — Very small p-values

**Expected:** p-values below 0.0001 display as `< .0001`.

```{r test34}
m34 <- lm(Sepal.Length ~ Petal.Length + Petal.Width + Species, data = iris)
tula(m34)
```

---

## Test 35 — Single predictor (minimal model)

**Expected:** Header and table format correctly with just one covariate row
plus the intercept.

```{r test35}
m35 <- lm(mpg ~ wt, data = mtcars)
cat("Narrow:\n")
tula(m35)
cat("\nWide:\n")
tula(m35, wide = TRUE)
```

---

## Test 36 — Ordered factor

**Expected:** Ordered factors are treated the same as regular factors — grouped
under a header row with indented levels.

```{r test36}
mtcars$gear_o <- factor(mtcars$gear, ordered = TRUE)
m36 <- lm(mpg ~ gear_o + wt, data = mtcars)
tula(m36)
```

---

## Test 37 — glm with factor and small sample (stress test)

```{r test37}
# Use only a subset of iris for a binomial model
iris_bin <- iris
iris_bin$is_virginica <- as.integer(iris_bin$Species == "virginica")
m37 <- glm(is_virginica ~ Sepal.Length + Sepal.Width,
           data = iris_bin, family = binomial)
cat("Narrow:\n")
tula(m37)
cat("\nWide:\n")
tula(m37, wide = TRUE)
```

---

## Test 38 — Error handling: unsupported object type

**Expected:** A clear, informative error message naming the unsupported class.

```{r test38}
tryCatch(
  tula(list(x = 1, y = 2)),
  error = function(e) cat("Error caught as expected:\n", conditionMessage(e), "\n")
)
```

---

# polr / ordered regression (MASS)

```{r polr-setup}
library(MASS)
mtcars$gear_ord <- factor(mtcars$gear, ordered = TRUE)   # 3 levels → 2 cutpoints
```

## Test 39 — polr: basic numeric predictors

**Expected:** `Ordered regression / Link: logistic` family label above header.
Header left: AIC, BIC, Log likelihood. Header right: N, McFadden R-sq.
Predictor rows use `z` / `P>|z|`. Cutpoints (`3|4`, `4|5`) appear after an
extra separator, with Coef. and Std. Err. populated but `z` and `P>|z|` blank.

```{r test39}
m39 <- polr(gear_ord ~ mpg + wt, data = mtcars, Hess = TRUE)
cat("Narrow:\n")
tula(m39, width = 72)
cat("\nWide (CIs on both predictors and cutpoints):\n")
tula(m39, wide = TRUE, width = 100)
```

---

## Test 40 — polr: factor predictor, factor grouping + cutpoints

**Expected:** Stata-style factor group header (`cyl`) with indented levels
in the predictor section, *and* cutpoints in the lower section. The two
sections must be cleanly separated.

```{r test40}
m40 <- polr(gear_ord ~ mpg + factor(cyl), data = mtcars, Hess = TRUE)
cat("Narrow:\n")
tula(m40, width = 72)
cat("\nref = TRUE:\n")
tula(m40, ref = TRUE, width = 72)
```

---

## Test 41 — polr: exp = TRUE (odds ratios, cutpoints unaffected)

**Expected:** Predictor rows show `exp(b)` / `DMSE`; column headers change.
Cutpoint rows are **not** exponentiated — they show raw values as before
(cutpoints are threshold parameters, not log-odds). A note about CIs being
suppressed should appear.

```{r test41}
cat("exp = TRUE:\n")
tula(m40, exp = TRUE, width = 72)
cat("\nexp = TRUE, wide = FALSE (no message):\n")
tula(m40, exp = TRUE, wide = FALSE, width = 72)
```

---

## Test 42 — polr: four-level outcome (three cutpoints)

**Expected:** Three cutpoint rows (`XS|S`, `S|M`, `M|L`) in the lower section.

```{r test42}
iris4 <- iris
iris4$size <- cut(iris$Sepal.Length,
                  breaks = quantile(iris$Sepal.Length, c(0, .25, .5, .75, 1)),
                  labels = c("XS", "S", "M", "L"),
                  include.lowest = TRUE,
                  ordered_result = TRUE)
m42 <- polr(size ~ Sepal.Width + Petal.Length + Species, data = iris4, Hess = TRUE)
tula(m42, width = 72)
```

---

## Test 43 — polr: probit link

**Expected:** Family label reads `Ordered regression / Link: probit`.
Output structure identical to logistic; only coefficient values differ.

```{r test43}
m43 <- polr(gear_ord ~ mpg + wt, data = mtcars, method = "probit", Hess = TRUE)
tula(m43, width = 72)
```

---

## Test 44 — clm (ordinal package, if installed)

**Expected:** Output structurally identical to the matching `polr` model.
Family label reads `Ordered regression / Link: logit`. Coefficients should
agree closely with Test 40 (minor differences from optimiser tolerance).

```{r test44}
if (requireNamespace("ordinal", quietly = TRUE)) {
  library(ordinal)
  mc44 <- clm(gear_ord ~ mpg + factor(cyl), data = mtcars)
  cat("clm (ordinal):\n")
  tula(mc44, width = 72)
  cat("\npolr (MASS) — same model for comparison:\n")
  tula(m40, width = 72)
} else {
  cat("ordinal package not installed — clm test skipped.\n")
}
```
